---
title: "Reading Notes"
author: "Hui Lin"
date: "Last Update: Wednesday, Dec 9, 2015"
output: 
 html_document:
  theme: united
  highlight: tango
  toc: true
  toc_depth: 5
  number_sections: true
---


[**Back to homepage**](http://linhui.org/)

# Reading List

It is my reading list since 2009. The reading notes are arranged according to book category.There are tons of paper notes need to be electrolyzed and I will keep working on it in my spare time (it will be very nice if Pioneer allows me to work on my reading notes during working hours......I am just dreaming.>_<) ......I know nothing about library science but the goal here is to make things more structured and easy to search which will be especially helpful when I am traveling. Good luck......   

My personal comments will start with "Hui:". Sometimes I summarize the contents with my own words. It is great if you find any of those notes useful for you as well. I thank all my friends who recommended great books to me. If you have any questions or awesome books that you keenly want to share, feel free to email me at: longqiman@gmail.com. Thank you!

```{r,echo=FALSE}
library(DT)
dat<-read.csv("/Users/happyrabbit/Dropbox/book/ReadingListHui.csv")
# Code used to assign ID
#dat<-dat[order(dat$CATE_CODE,decreasing=F),]
#library(nnet)
#res<-class.ind(dat$CATE_CODE)
#for (i in 1:ncol(res)){
#res[,i]<-res[,i]*cumsum(res[,i])/100
#}
#dat$ID<-paste(dat$CATE_CODE,apply(res,1,sum),sep="")
#setwd("/Users/happyrabbit/Dropbox/book/")
#write.csv(dat,"ReadingListHui.csv",row.names=F)
```

```{r,echo=FALSE}
datatable(subset(dat,select=c("Name","ID","Category","Author","Progress","Priority")))
```


- **Name**: Book name
- **ID**: Book index number 
- **Category**: Book category  
- **Author**: Author of the book
- **Progress**: My reading progress(from 0% [haven't started] to 100% [finished])
- **Priority**: My reading priority

## Basic Statistical Analysis

Here is a plot for counts of books in each category......Obviously, my favorite is "Philosophy and Psychology" and I am not very interested in "Politics"......Statistics (31), Data Science (5) and IT(7) [**SDT** area], all these three added together is about the size of "Business & Economics". I am a little surprised. Some possible insights are (not all of them necessary to be true):
 
1. Professional area/degree don't tell how a person spend time
1. Scientists read more journal papers and technique reports in corresponding area than books
1. There are not as many books in **SDT** as in some other areas   
1. I didn’t spend enough time in **SDT** 
1. I need to work harder on **SDT** 

```{r, echo=FALSE}
dat$Category[dat$Category=="Novels and Plays-detective"]<-"Novels and Plays"
dat$Category[dat$Category=="Novel"]<-"Novels and Plays"
booktb<-data.frame(table(as.character(dat$Category)))
names(booktb)<-c("Category","Counts")
booktb<-booktb[order(booktb$Counts,decreasing = T),]
library(ggplot2)
ggplot(booktb, aes(x=reorder(Category,Counts), y=Counts, fill=Category)) + 
  geom_bar(stat="identity")+ coord_flip()+ ylab("Counts") + xlab("Category")+ theme(legend.position="none")
```

Here is a plot showing the percentage of books I have started (or finished) across different categories.

```{r, echo=FALSE}
Progress<-rep("Started",nrow(dat))
idx<-which(dat$Progress=="")
Progress[idx]<-"Not-Started"
dat$Status<-Progress
ggplot(dat, aes(Category,fill=Status)) +
geom_bar(position="fill")+ coord_flip()+ ylab("Percentage") + xlab("Category")

```

```{r, echo=FALSE}
#bookp<-data.frame(table(dat$Category,dat$Progress))
#head(bookp)
#booktb<-booktb[order(booktb$Counts,decreasing = T),]
#booktb
```

# Philosophy

## The Tibetan Book of Living and Dying [西藏生死书，Sogal Rinpoche]

> Hui: 这本书让你严肃系统的思考死亡，从藏传佛教的角度讲述生死。这本书意在写给西方人看的，结合了中西方思想，时而引入基督教的例子，相对其它佛教书籍更加通俗易懂。书的核心观点是我们从出生的那一刻开始就在准备死亡，好好活着是为了最终能够好好死去。书中指出一切都是无常，看穿我执的虚妄，理解无常，回归本性。虽然对许多地方有疑问，但还是非常推荐这本书。看过之后或许能向不畏死，亦能好好活跨进一步。

### Living [生]

Karma: 业力  
Phowa: 颇瓦法  
Samsara: 轮回世界
Rigpa: 本觉
Nangpa: 佛教徒，内省的人
Luminosity: 觉明
Wisdom-energy: 智慧能
Heart-center: 心轮
Wisdom-channels: 智慧脉
Karmie winda: 业风
Prana: 呼吸

#### In the Mirror of Death [在死亡的镜子中]

- The disastrous effects of the denial of death go far beyond the individual: They affect the whole planet. Believing fundamentally that this life is the only one, modern people have developed no long-term vision. So there is nothing to restrain them from plundering the planet for their own immediate ends and from living in a selfish way that could prove fatal for the future. （否定死亡的可怕影响力，绝不止于个人层面，它影响着整个地球。由于大多数人相信人生就只有这么一世，现代人已经丧失长远的眼光。因此，他们肆无忌惮地为着自己眼前的利益而掠夺地球。）

#### Impermanence [无常]

- To practice death is to practice freedom. A man who has learned how to die has unlearned how to be a slave. [Montaigne]
- Death is a vast mystery, but there are two things we can say about it: (1) It is absolutely certain that we will die; (2) It is uncertain when or how we will die.
- Why do we live in such terror of death? Because our instinctive desire is to live and to go on living, and death is a savage end to everything we hold familiar.
- Perhaps the deepest reason why we are afraid of death is because we do not know who we are.
- Without our familiar props, we are faced with just ourselves, **a person we do not know, an unnerving stranger with whom we have been living all the time but we never really want to meet**.

> Hui: 我们被各种各样的刺激、快感催眠(hypnotize)，生活渐渐沦为手段淹没目的的过程。不知道自己是谁，不知道为什么活着。

- Just look at your mind for a few minutes. You will see that it is like a flea, constantly hopping to and fro. 
- The birth of a man is the birth of his sorrow. The longer he lives, the more stupid he becomes, because his anxiety to avoid unavoidable death becomes more and more acute. What bitterness! He lives for what is always out of reach! His thirst for survival in the future makes him incapable of living in the present. (人之生也，与忧俱生。寿者昏昏，久忧不死。何苦也！其为形也，亦远矣！《庄子至乐篇》)
- Our lives are monotonous, petty, and repetitive, wasted in the pursuit of the trivial, because we seem to know of nothing better.....The pace of our lives is so hectic that the last thing we have time to think of is death. 
- As a Tibetan saying goes:"Tomorrow or the next life, which comes first, we never know."
- Discipline is to do what is appropriate or just; that is, in an excessively complicated age, to simplify our lives......the only serious goals in life are **"learning to love other people and acquiring knowledge(学习爱别人和获得知识)"**......**Whatever we have done with our lives makes us what we are when we die.(我们一生的所作所为，造就了我们去世时的模样。)** And everything, **absolutely everything counts**.
- In our minds changes always equal loss and suffering. And if they come, we try to anesthetize ourselves as far as possible. We assume that permanence provides security and impermanence does not. (我们害怕变化)
- The past is past, the future not yet risen, and even the present thought, as we experience it, becomes the past. The only thing we really have is now......Has my understanding of death and impermanence become so keen and so urgent that I am devoting every second to the pursuit of enlightenment?

#### Reflection and Changes [反省与改变]

- There is one way, and one way only, out of samsara's ceaseless round of birth and death, which is the path to liberation.
- Those with dualistic perception（分别心） regard suffering as happiness, like they who lick the honey from a razor edge.
- We may idealize freedom, but when it comes to our habits, we are completely enslaved.
- Learning to live is learning to let go.
- There is nothing wrong with the desire to be happy, but what we grasp on to is by nature ungraspable. The Tibetans say you cannot wash the same dirty hand twice in the same running river, and, "No matter how much you squeeze a handful of sand, you will never get oil out of it."
- How can we work to overcome attachment? Only by realizing its impermanent nature; this realization slowly releases us from its grip. 

> Hui: understand and accept uncertainty. being mortal

- Nothing has any **inherent** existence of its own when you really look at it, and this absence of independent existence is what we call "emptiness".

> Hui: It reminds me the beginning of Ecclesiastes.   
**[Ecclesiastes 1:2-10]** "Everything is meaningless", says the Teacher, "completely meaningless!" What do people get for all their hard work under the sun? Generations come and generations go, but the earth never changes. The sun rises and the sun sets, then hurries around to rise again. The wind blows south, and then turns north. Around and around it goes, blowing in circles. Rivers run into the sea, but the sea is never full. Then the water returns again to the rivers and flows out again to the sea. No matter how much we see, we are never satisfied. No matter how much we hear, we are not content. History merely repeats itself. It has all been done before. Nothing under the sun is truly new. Sometimes people say, "Here is something new!" But actually it is old; nothing is ever truly new.

- Always recognize the dreamlike qualities of life and reduce attachment and aversion. (认知生命有如梦幻，减少执著和嗔怨)

> Hui: 无所不有是**全**，一无所有是**空**。全是面子，空是里子。什么都是也就无所谓是什么，等于什么都不是，意识到这一点，就可以放下了。

#### The Nature of Mind[心性]
- "the homage of the View" It is a devotion that springs spontaneously from seeing the View of the nature of mind.(“知见皈依”这是从看到心性的知见而当下产生的恭敬心。)
- **Life and death are in the mind, and nowhere else.**

> Hui: It resonates what Bible says. Jesus came to show us the way, teach us the truth and invite us to find life. As Jesus said to the Samaritan woman:"Anyone who drinks this water will soon become thirsty again. But those who drink the water I give will never be thirsty again. It becomes a fresh, bubbling spring within them, giving them eternal life." Indeed, life and death depend on your mind, your faith. 

- There are many aspects to the mind, but two stand out.   
     1. Ordinary mind, called by the Tibetans _sem_. One master defines it:"That which possesses discriminating awareness, that which possesses a sense of duality--which grasps or rejects something external--that is mind. Fundamentally it is that which can associate with an 'other'--with any 'something', that is perceived as different from the perceiver."(凡夫心，分别，相对心)
     1. Then there is the very nature of mind, its innermost essence, which is absolutely and always untouched by change or death. At present it is hidden within our own mind, our _sem_, enveloped and obscured by the mental scurry of our thoughts and emotions.(本性，心的底蕴，不受凡夫心影响。)
- The nature of mind is the very root itself of understanding. In Tibetan we call it _Rigpa_, a primordial, pure, pristine awareness that is at once intelligent, cognizant, radiant, and always awake. It could be said to be the knowledge of knowledge itself. (心性是了解的基础。)
- When a much larger number of people know the nature of their minds, they'll know also the glorious nature of the world they are in, and struggle urgently and bravely to preserve it. It's interesting that the word for "Buddhist" in Tibetan is _nangpa_. It means "insider-er": someone who seeks the truth not outside, but within the nature of mind.
- The central truth of Buddha's teaching: that we are all already essentially perfect.

> Hui: I don't agree that we are already essentially perfect.

#### Bringing the Mind Home [把心带回家]
- In fact, we are already perfectly trained by and for samsara, trained to get jealous, trained to grasp, trained to be anxious and sad and desperate and greedy, trained to react angrily to whatever provokes us. We are trained, in fact, to such an extent that these negative emotions rise spontaneously, without our even trying to generate them. 
- We will find that with time, patience, discipline and the right training, our mind will begin to unknot itself and know its essential bliss and clarity. [只有有耐心，纪律和正确的训练，我们的心将开始解开它自己的结，并认识它自己本有的喜悦和清明]
- Because from the mind are derived all fears and immeasurable sorrows.
- We are fragmented into so many different aspects. We don't  know who we really are, or what aspects of ourselves we should identify with or believe in. So many contradictory voices, dictates, and feelings fight for control over our inner lives that we find ourselves scattered everywhere, in all directions, leaving nobody at home.Meditation is **bringing the mind home**.
- Three things make all the difference between your meditation being merely a way of bringing temporary relaxation, peace, and bliss or of becoming a powerful cause for your enlightenment and the enlightenment of others:
      1. **Good in the Beginning:** springs from the awareness that we can all sentient Beings fundamentally have the buddha nature as our innermost essence, and that to realize it is to free of **ignorance** and to put an end, finally, to **suffering**. [believe in the equality of all beings]
      1. **Good in the Middle:** frame of mind with which we enter into the heart of the practice, one inspired by the realization of the nature of mind, from which arises an attitude of non-grasping, free of any conceptual reference whatsoever, and an awareness that all things are inherently "empty", illusory, and dream-like.
      1. **Good at the End:** the way in which we bring our meditation to a close by dedicating all its merit and praying with real fervor......Merit is the positive power and benefit, the peace and happiness that radiate from your practice.

- Three sacred principles make meditation truly enlightening and powerful:
     1. the skillful motivation [善巧的动机]
     1. the attitude of non-grasping that secures the practice [让修行成功的不执着的态度]
     1. the dedication that seals it [结束时的回向]
- The practice of mindfulness, of bringing the scattered mind home, and so of bringing the different aspects of our being into focus, is called "Peacefully Remaining" or "Calm Abiding" which accomplishes three things:
     1. all the fragmented aspects of ourselves, which have been at war, settle and dissolve and become friends. In that settling we begin to understand ourselves more, and sometimes even have glimpses of the radiance of our fundamental nature.[自己被撕裂成碎片的所有部分，过去一直都处在战争之中，现在则安住而定下来，而溶化，而变成朋友。在那种安定之中，我们开始了解自己，有时候甚至还可瞥见自性的光芒。]
     1. the practice of mindfulness defuses our negativity, aggression, and turbulent emotions, which may have been gathering power over many lifetimes. [正念的修行可以舒缓我们多生多世以来所累积的负面心侵略性和混乱情绪。] 
     1. this practice unveils and reveals your essential Good Heart, because it dissolves and removes the unkindness or harm in you. [这种修行揭开并显露出你根本的善心，因为它消除了你心中的仇恨或伤害。]
- To _release_ means to release mind from its prison of grasping, since you recognize that all pain and fear and distress arise from the craving of the grasping mind.
- meditation is nothing other than getting used to the practice of meditation.
- The mantra "Om Ah Hung Benza Guru Pema Siddi Hung" is uniquely powerful for peace, healing, transformation and protection in this violent, chaotic age. 
- There is a famous saying:"_If the mind is not contrived, it is spontaneously blissful, just as water, when not agitate, is by nature transparent and clear._"

> Hui: But why is human heart so easily disturbed? we are BORN WITH SIN!

- In meditation, as in all arts, there has to be a delicate balance between relaxation and alertness.
- Ancient meditation instructions:
     1. at the beginning thoughts will arrive one on top of another, uninterrupted
     1. steep mountain waterfall
     1. water in a deep narrow gorge
     1. still and placid ocean ruffled by only the occasional ripple or wave

- So have a spacious, open and compassionate attitude toward your thoughts and emotions, because in fact your thoughts are your family, the family of your mind......thoughts are like the wind; they come and go. The secret is not to "think" about thoughts, but to allow them to flow through the mind, while keeping your mind free of afterthoughts......there is gap between each thought......the Rigpa, the nature of mind in revealed in the gap. So the work of meditation is to allow thoughts to **slow down**, to **make that gap become more and more apparent**.
- Traditionally it's said that for a real practitioner, it's not the negative experiences but the good ones that bring obstacles.
- Then after meditation, it's important not to give in to the tendency we have to solidify the way we perceive things. When you do reenter everyday life, let the wisdom, insight, compassion, humor, fluidity, spaciousness, and detachment that meditation brought you pervade your day-to-day experience. (在禅修之后，不要回到我们易于将事物固化的习气。当你重新进入日常生活时，要让禅修所带给你的智慧、洞察力、慈悲、幽默、柔软、旷达和自在充满你每天的生活经验。)
- When I eat, I eat; When I sleep, I sleep. (这就是禅修)
- Meditation is an art and you should bring to it an artist's delight and fertility of invention.....Be alert for any sign of beauty or grace.

#### Evolution, Karma, and Rebirth [演化、业与轮回]

Shelley 雪莱  
Balzac 巴尔扎克  
Voltaire 伏尔泰  

- How much would it help us, I sometimes wonder, if we did remember them? Couldn't that just confuse us even more?
- Dalai Lama: " _**The basis on which Buddhists accept the concept of rebirth is principally the continuity of consciousness.**_ "

## On the Immortality of the Soul [论灵魂, Marcus Tullius Cicero]

- 最适合老年的养身之道莫过于研究学问和培养美德，一个人随时注意培养美德，在他度过漫长的一生时，便会收到惊人的结果。

## Gravity and Grace [重负与神恩, Simone Weil] 


> Hui: 这是我在2012年读的一本书，书很薄但很实，没有废话。Weil认为，不幸是绝对的。人的存在的不幸是无法消除的。她尖锐的地指出任何社会形态——哪怕是最近完美的社会形态都不能消除人的不幸，不幸不同于不义，所以革命不能代替人的救赎，而只能掩盖不幸，忽略看轻人的不幸，这也就是柏拉图所谓的猛兽式的社会性残忍。“爱是一种神圣的东西。若深入内心，就会将它撕裂。人心被创造出来就是供撕裂的。当它被其它东西撕裂时，就是最可悲的浪费。但它宁可被其它东西撕裂而不是被神圣的爱。因为神圣的爱只撕裂自愿被撕裂的心。这种自愿是困难的。”从一个基督徒的角度，我对这句话的理解是我们只有摒弃过去的自己（也就是所谓的撕裂），将自己交给神，相信神，才能得到永恒的神恩。神恩的翻译是Grace，我及其喜欢这个关于Grace的定义： “Grace is God's kindness, his love, his care, his work on our behalf, his blessings, his gifts, his goodness, his forgiveness, and his salvation. But it is more than that--it is all these things **when they are undeserved**, when they are **pure gift**”.   只有来自神恩的爱才能够改变我们，改变接受神恩的人，也改变了这些接受神恩后向其他人传递神恩的人。为什么放弃原来那个自己那么困难？因为骄傲，我们放不下内心的骄傲，便无法接受神的恩典。这种放下和自愿被撕裂当然是困难的，否则神恩来的太便宜了。    
此外，作者认为包含真理的思想存在于不同的宗教经典，文学与科学著作中，真理遵循不同的途径显示在人们的精神中。比如希腊几何学和诗歌，中国的道教，埃及的俄赛里斯教，印度佛经等，都融合了圣经所包含的真理。

- 两种力量主宰着宇宙：光(light)和重力(gravity)。重负，一般地说，人们期待他人的事是我们身上的重负效果决定的；人们从他人那里得到的由他人身上重负效果所决定。**为何一旦有人表示有一点，或非常需要别人时，别人会选择远离？重负所致。** 灵魂的一切自然的运动受物质万有引力一类的规律制约。唯有神恩例外。

> Hui: 神的爱是无条件的。

- 在这种情况下，我至少由有好几次忍不住说出伤人之语。向重负屈服了。这是大逆不道。话语的功能就是如此被滥用，话语是用来表达事物关系的。
- 伤害他人，就是要从中得到什么。得到什么呢？当伤害他人时，赢得了什么？人们扩展了自己。发展了自己。在他人身上建立虚无以填平自身的虚无。
- 若想到上帝不存在而爱上帝，他将会显示他的存在。

> Hui: 我们对上帝的爱也需要是无条件的。

- 一切虚空，（不被接受）产生仇恨、刻薄、苦涩、积怨。人们盼望自己所恨的遭到恶报，以及人们想象的饿恶重建起了平衡。
- 创造是一种矮的行为，它是永久的。我们存在的每时每刻都是上帝对我们的爱。但上帝只能爱自己。他对我们的爱是通过我们去爱他自己。因此，是他赋予我们存在，他爱我们而甘愿不存在。......我们的存在只是由于他的期待，由于我们不同意不存在造成的他永久地向我们乞求他赋予我们的这个存在。他把存在给予我们是为了向我们乞求它。......正是上帝出自爱而离开我们，以便我们能爱他。因为倘若我们直接沐浴在他的爱的辉映下而没有空间、时间和物质的掩护，我们就会像阳光中的水一样蒸发掉；我们就不会有足够的我可以为了爱而放弃那个“我”。
- 只要我们尚未明白我们有底，我们便是无底的桶。......我们只拥有自己弃绝的东西。人们失去了自己不愿意弃绝的东西。在此意义上，不经由上帝，人们便不能拥有任何东西。
- 上帝并不仅只有一次使自己成为血肉，他每天都使自己成为物以共给人，供人食用。反之亦然，人由于劳累，不幸和死亡而成为物，并被上帝食用。怎么能拒绝这种相互性？
- 因为不幸的伤口和不幸所引起的屈辱使人认识人间疾苦，这种认识乃是一切智慧之门。
- 人的生命中只有两个完美的赤裸和纯洁的时刻：出生和死亡。
- 在没有我们的情况下创造了我们的人并不会在没有我们的情况下拯救我们——Saint Augustine  
幕，就是人的苦难：甚至对于基督也有帷幕。......扎根于漂泊不定之中。
- 我身上具有的精力，天赋等等，又有何用？我受够了，可以消失了。......当我在某处时，我的呼吸，我的心跳，会玷污天上和地下的宁静。
- 必然的两面：行使必然和承受必然。阳光(sunshine)和十字架(cross)。......服从必然而非服从束缚。......行为是天平的指针。不应触碰指针，而是触碰砝码。......惟有完全的超脱才能使人透过骗人的价值的迷雾看到赤裸的事物。

> Hui: 如何完全超脱呢？

- 我们接受在我们面前显现的虚假的价值，当我们认为在行动时，实际上我们静止未动，因为我们依然处在同样的价值体系中。......有关尘世事物的错觉并不涉及其存在，而是其价值。
- 我们身上源于撒旦的东西便是想象。

> Hui: I don't understand it.

- 期限，对于文明来说是以世纪计数，对于个人来说是以年，数十年计数，它具有一种不适者消亡的达尔文式的功能。
- 在屈辱中，傲慢使内在的谎言越来越大。......所有无价值的东西都逃避光照。在尘世，人可以借肉体隐藏自身。死后就办不到了。人就赤裸裸地把自己交付给光照。

> Hui: 和西藏生死书里的观点类似。

- 人们不可能面对面见到上帝而不死，但人们并不愿死。......肉体并非是使我们远离上帝的东西，它是我们遮在面前的帷幕以在我们和上帝之间制造屏障。

> Hui: 人一边说爱着上帝，要追随上帝，一边却又紧紧抓住尘世的光阴。我至今也不明白为什么。或许在活着的时候就是为了要努力的修行，使我们能够在死时见到上帝而不逃离，抓住那光明，并且于光明同在。所以我们在准备，一直在准备，我们抓住尘世，是因为觉得自己还没有准备好。

- 渴望躲避孤独是一种胆怯行为。......模仿上帝是一种不良企图。
- 恶，当人们身处恶中时它并不被感知为恶，而是被感知为必然性或者责任。
- 只有在无望使距离的意识变得无法容忍并且将痛苦转变为仇恨时，相应的犯罪才会产生。
- 人们无法注视人可能做的恶和可能承受的恶的规模而不感到恐惧。......只有处在他人无法再伤害我们的境地时，我们才可能厌恶对他人造成伤害（于是爱他人就像爱过去的自己一样是有限的）

> Hui: 非常喜欢这两句

- 若这世上没有不幸，我们会以为自己在天堂。有一种不幸是：人们无力承受它延续下去，也无力从中摆脱出来。......有两种想法会减轻一点不幸。一是不幸即可就会停止，另一种不幸永不止息。
- 苦难，教育和转化。被授予宗教奥义者不应是学到些什么，而是在他们自身实现某种转化，这种转化使他们能接受教育。
- 必须通过快乐，拥有了真实的揭示才能在痛苦中获得真实。否则，生活只是一场或深或浅的噩梦。......必须在虚无和虚空的困难中努力找到更为充实的现实。同样，应当热爱生活以更加热爱死亡。
- 战争和情欲是人中间的两大幻想和谎言之源。两者的混合是最大的不纯。
- 基督治愈残疾者，使死者复活等等，这些是他使命中不足道的、人间的、几乎卑下的部分。基督的使命的超自然部分，则是血泪，是抚慰人的愿望并未实现，是祈求得到宽容，是被上帝抛弃的感情。......“My God, my God, why have you abandoned me? 我的上帝，我的上帝，你为何离弃我？”这就是基督成为某种神圣东西的明证。
- 穿过时间和空间的无限厚度，上帝为找到灵魂并诱惑它而精疲力竭。如果灵魂表示了纯净而全面的赞同，即使是闪电般的一瞬间，上帝便政府了灵魂。当灵魂变成完全归于他的东西时，上帝便抛弃它。他让灵魂孤身独处。轮到灵魂穿过时间和空间的无限厚度，摸索寻找灵魂所爱者。就这样，灵魂从相反方面重做上帝朝它而来的旅行。这就是十字架。
- 基督的仁慈宽厚，就是上帝与造物之间的距离。......中介的功能，在其自身，意味着左右为难。
- 上帝把自己奉献给人，作为强大无比者或者作为完美无缺者——由人自己选择。
- 基督十字架的秘密在于某种矛盾中，因为这即是一种自愿的奉献，又是一种他身不由己受到的惩罚。

> Hui: “自愿”源自于上帝的仁慈和爱；“身不由己”则因为人性中的罪。

- 她否认上帝在自然中留下的不确定性和“无根据”的余地，而这种余地使自由和奇迹得以进入尘世。同样，在事实上，重负确实是强大无比的：圣.托马斯承认，大部分人的行为是受命于感官的盲目的欲望，并屈从于星辰的决定性的.[原编者注]

- 惟一不受偶然性支配的善是尘世之外的善。要知道_**最珍贵的东西并不扎根于生存中**_。这是美的。为什么？它把灵魂抛到时间之外。想生一个白如雪，红似血的孩子的女人，得到了这样的孩子，但她死了，孩子托付给了继母。

- 凡是存在的东西绝对不值得爱。因此，应爱不存在之物。

> Hui:不太理解这点，那么神存不存在呢？抑或这里讲的的世俗意义的存在，而非精神。

- 信念（这里所说的是对自然的一种超自然的阐释）是一种建立在超自然经验基础上的通过类比做出的**臆测**。......神秘主义是人类品性的惟一源泉。因为，不相信在尘世的幕后有无限的慈悲，或是相信这种慈悲在幕前，两者都使人变得残忍。

> Hui:也就是说，以作者看信念是一种主观想象，而非客观存在。

- 只有当我们在内心深处需要某种表示什么意义的声音，当我们呼叫以求得回音而我们却得不到回音时，只有这时，我们才触及上帝的沉默。
- 在两个不曾体验过上帝的人中间，否认上帝的人也许离上帝最近。

> Hui:怀疑否认比不假思索的盲信要好。

- 专注，从其最高程度上来说同祈祷是一回事。它意味着信念和爱。专注丝毫不分心就是祈祷。高度的专注就是构成人的创造才能的东西，而惟有宗教的专注才是高度的专注。......若人们不把注意力从上帝的启示上挪开，若人们不拒绝这种启示，那么上帝的启示必定会不可抗拒的发生。对于上帝的启示，并无选择可做，只需要不拒绝承认它的存在。怀着爱把专注专向上帝（或转向更低层次，一切真正美的东西），这使一些事难以实现。这就是灵魂中祈祷的不起作用的行文。我不必担心不拼命努力。条件仅仅是不自欺并要专心。
- 极端的纯洁性可注视纯洁，也可注视非纯洁；非纯洁性两者均不能；前者使它害怕，后者将它吸收。

> Hui:纯洁具有包容吸收的能力。海纳百川，有容乃大。能被玷污的，是因为原本就不够干净；能被伤害的，是因为原本就不够强大。

- 要触及不可能，必须完成可能。应在规定的时间完成职责，以确信外部世界的实在。应确信时间的实在，不然，就在幻想。
- 假如在此之后和余生之中自己会成白痴，真理却继续存在。
- 若人人都始终按照自己所读的正义来行事，公正与不公正之间的差别又是什么？
- 美：是一种人们看着它而不向它伸手的水果。

> Hui: 占有有可能既是破坏。

- 我们一定是犯下了使我们被诅咒的罪过，因为我们已失去了宇宙的一切诗歌。

> Hui: 这句话看了好难过啊。

- 艺术只有在大混乱中才能产生......因为不幸会使许多事情变得简单。
- 现代生活全由过度摆布，过度侵入一切：行为和思维，公众和私人生活。由此造成艺术的堕落。任何地方都没有平衡。时光在流逝中，销蚀，摧毁了世俗的东西。因此，在过去中有比现在更多的永恒。
- 在人所爱和所恨之间是否有同一性？人所恨的东西，当它出现另一种形式时，人们会有必要去爱它吗？反之呢？革命的经久不灭的幻想在于认为由于权利的受害者是无辜遭受着暴力。倘若把权力放在他们手中，他们就会公正地使用它。然而除了接近神圣的人，受害者如同刽子手一样被权利玷污。剑柄上的恶传送到了尖端。如此般登上巅峰的受害者由于变化而陶醉，他们会同样作恶或是更多地作恶，然后又马上跌倒在地。
- 劳动使人疲乏不堪地感受到了像球一样踢回来的合目的性现象。

## Tolerence [宽容，Van Loon]
### The Tyranny of Ignorance [无知的暴君]

- It follows that a society in which everything happens as the result of the direct personal interference on the part of an invisible being must depend for its continuted existence upon a strict obedience of such laws as seem to appease the wrath of the Gods.  
The word **taboo** is of Australian origin.
[在一个社会中，如果任何事情都被认为是由看不见的生灵操纵的，那么社会要维持下去，就必须绝对服从能平息神灵怒火的律法。]

> Hui: I wonder more about who is going to give the law and if God is the one, how are we supposed to know the laws we are given are really from God. I don't want to worry about the necessity of laws.

- Whether the taboo was an _**invention of the priests**_ or _**the priesthood was created to maintain the taboo**_ is a problem which had not yet been solved. As tradition is much older than religion, it seems more than likely that taboos existed long before the world had heard of sorcerers and witchdoctors. [究竟是祭司发明了禁忌，还是为了维护禁忌才产生了祭司，这是尚待解决的问题。由于传统比宗教更为源远流长，因此很可能早在男巫师和女巫婆问世之前禁忌就存在了。]

> Hui: According to the author, does he mean that **the priesthood was created to maintain the taboo**?

What we sometimes mistake for tolerance was merely indifference caused by ignorance. The struggle for tolerance did not begin until after the discovery of the individual. And the credit for this, the greatest of all modern revelations, belongs to the Greeks. [我们有时看到的宽容，实际上是由于无知导致的漠不关心。为宽容的斗争直到个性被发现后才开始，在现代最伟大的新发现中，个性发现这一荣誉应归功于希腊人。]

### The Greeks [希腊人]

According to the best knowledge of modern scientists, life (animate existence as differentiated from inanimate existence) began when for once all physical and chemical elements were present in the ideal proportion necessary for the creation of the first living cell. Translate this into terms of history and you get this: _“A sudden and apparently spontaneous outbreak of a very high form of civilization is only possible when all the racial, climatic, economic and political conditions are present in an ideal proportion or in as nearly an ideal condition and proportion as they can be in this imperfect world."_

[根据现代科学家的研究成果：当所有物理和化学的成分都达到形成第一个细胞的理想比例时，生命便开始了。把上面的话应用到历史学的概念，就是：“只有当所有种族、气候、经济和政治条件在不健全的世界中都达到或接近一种理想比例时，高级形式的文明才会突然地貌似自发地脱颖而出。”]

# Psychology

## The Theory of Moral Sentiments [Adam Smith]
### Of the Propriety of Action
#### Of the Sense of Propriety
##### Of Sympathy
1. Principles in the nature, the emotion which we feel for the misery of others when we either see it, or are made to conveive it in a very lively manner. (人性中的原始感情)
1. 原因：看到引发那种感情的处境
1. 恐惧死亡：对死者同情。我们把自己还活着的灵魂塞进他们已失去活力的躯壳里，然后设想在这种情况下我们自己将会有什么样的情绪。正是该错觉，在我们死后无疑不可能给我们带来任何痛苦的那些情况，在我们活着时想起来却让我们心痛不已。

##### Of the Pleasure of Mutual Sympathy [论彼此同情的快感]
1. 最让我们愉快的事，显然莫过于发现他人的感觉和我们自己心理全部情绪一致；而最让我们震惊的，也莫过于发现他人和我们完全没有同感......同情感活化喜悦，缓和悲伤......我们更加渴望向朋友倾诉我们心理的不愉快；他们同情我们的不愉快，比同情我们的喜悦， 会让我们得到更大的满足，而他们对我们的不愉快缺乏同情感，则比他们对我们的喜悦缺乏同情感，更加另我们震惊。

## Personality [人格心理学, Jerry M. Burger, 7th Edition]
### What is Personality?

**人格**可以定义为源于个体身上的 _稳定_ 行为方式和 _内部过程_ 。该定义中有两个需要注意的点：

      1. 人格是稳定的，我们可以跨时间、跨情境地来审查这些稳定的行为方式。
      2. 内部过程， 它是从人的内心发生，影响人行为、感觉的所有情绪、动机和认知过程。

> Hui: 该定义没有提到环境，而是着眼与个体层面，研究那些在不同情境下相对稳定的行为方式和内部心理过程。但是环境对人格还是会产生影响的，只是程度不同，这与背后存在共性并不矛盾。

## Social Psychology [社会心理学, David G. Myers, 8th Edition]
### Introducing Social Psychology

## People of the lie [M Scott Peck]

### Introduction: Handle with care

- Remember Saint Augustine's advice to hate the sin but love the sinner. [憎恨罪恶，但要爱有罪的人]
- Great evil has been committed throughout the centuries--and is still committed--by nominal Christians, often in the name of Christ.
- There are hundreds of thousands who go to Christian churches every Sunday who are not the least bit willing to be displeasing to themselves, serenely or otherwise, and who are not, therefore, for Jesus a pleasant place of shelter. Conversely, there are millions of Hindus, Buddhists, Muslims, Jews, atheists and agnostics who are willing to bear that trial. 

### The man who made a pact with the devil
- obsessive-compulsive neurosis （强迫妄想型精神官能症）
- the pattern of unwanted thoughts and the taking of undesired actions

### Toward A Psychology of Evil

- While some seek in religion an escape from mystery, for others religion is a way to approach mystery. The latter are not loath to employ the **reductionistic（还原论，简化论）** methods of science, but they are also not reluctant to use more integrative "right brain" means of exploration: meditation, intuition, feeling, faith, and revelation. For them bigger the mystery, the better.
- The problem of evil can hardly be separated from the problem of goodness. Were there no goodness in the world, we would not even be considering the problem of evil.
- It is as if we automatically assume this is a naturally good world that has somehow been contaminated by evil......If we seriously think about it, it probably makes more sense to assume this is a naturally evil world that has somehow been mysteriously "contaminated" by goodness, rather than the other way around. The mystery of goodness is even greater than the mystery of evil.
- Thus we may "break" a horse or even a child without harming a hair on its head. Erich Fromm was acutely sensitive to this fact when he broadened the definition of **necrophilia （恋尸癖）**to include the desire of certain people to control others-----to make them controllable, to foster their dependency, to discourage their capacity to think for themselves, to diminish their unpredictability and originality, to keep them in line. Distinguishing it from a **"biophilic" person（具有生物自卫本能的人）**, one who appreciates and fosters the variety of life forms and the uniqueness of the individual, he demonstrated a "necrophilic character type" whose aim is to avoid the inconvenience of life by transforming others into obedient automatons, robbing them of their humanity.....Evil is that force, residing either inside or outside of human beings, that seeks to kill life or liveliness. Goodness is that which promotes life and liveliness.（弗洛姆广义的界定“恋尸癖”时，增列了某些人对他人的控制欲：使他人受控制，增强依赖度，削弱其主动性，接受管束。弗洛姆将“恋尸癖性格的人”和“具有生物自卫本能的人”加以区分：前者将他人改变为顺从的机器人，剥夺他们的人性，借以回避人生的艰难；而后者则承认并鼓励生命的多样变化，以及“人”独有的特性。）
- A psychology of evil must be a religious psychology......it must not only embrace valid insights from all religious traditions but must also recognize the reality of the "supernatural".
- Having fled the **Jewish persecution** of the Hitler regime, the psychoanalyst **Erich Fromm** spent much of the rest of his life studying the evil of **Naziism**. He （_原书中讲他是第一个也是唯一一个确定邪恶人格类型的科学家，此书写与1983年，这个说法已经不正确了_）.......to identify an evil personality type, to attempt to examine evil people in depth, and to suggest that they be studied still further.
- The great Jewish theologian **Martin Buber** distinguished between two types of myths about evil. One type conerns people in the process of "sliding" into evil. The other concerns those who have already slid, "fallen victim" to and been taken over by "radical" evil.

## Psychobabble [Stephen Briers]
### What's so wrong with popular psychology?

The author pointed out that more of us turn to self-help books for answers to lives that feel in need of fixing. The phenomenon indicates our rising levels of _insecurity_ and _self-doubt_ and the stealthy(悄然的，秘密的) psychologising of American culture as a whole. Self-help industry is meme of popular psychology. **Meme** is defined by **Richard Dawkins** in his _The Selfish Gene_ as "an idea, behaviour or style that spreads from person to person within a culture". It is like today's "Big Data" or "Data Science"......The major selling points of self-help book is to keep things simple and manageable. The social environment is complex. There are innumerable variables contribute to even a simple human activity. According to **"chaos theory"**, even small local variations can produce a truly bewildering variety of outcomes--so great in fact as to render prediction virtually impossible, even in a closed, deterministic system. 

> Hui: In the era of "Internet of Things", everything is connected. A slight move in one part may affect the situation as a whole. The consequence can be amplified/changed through the network. It is getting harder to predict and control. We badly need recipe to simplify this complicating world. At least, myself always wonder. The principle of **Occam's razor** advocates the virtue of parsimony. In statistical world, it means when two models provide similar results, always choose the simpler one. However, for our current situation, I agree with the author that even the most economical explanations at our disposal may still be too complicate. 

> Oscar Wilde: The truth is rarely pure and never simple

- In the mysterious world of particle physics, Superstring Theory remains the most promising candidate to provide us with a workable "Theory of Everything". This is the Grail of modern physics, the theoretical framework that will finally allow physicists to reconcile the uneasy bedfellows of quantum physics and general relativity. However as Brian Greene points out in _The Elegant Universe_, although the theory looks sound, the maths involved is proving so complex that even the best mathematical brains in the world are currently struggling to make the highly convoluted sums add up.

> Hui: I don't think it is a good example here. The general relativity also looks elegant but is mathematically hard to prove. An example on how the increasing information availability complicates people's decision making may fit better here. 
 
> Hui: I agree that the world is complicated. But what can we do?

### Myth 1: The root of all your problems is low self-esteem
### Myth 2: Let your feelings out!
### Myth 3: Emotional intelligence is what really counts
### Myth 4: Let your goals power you towards success!
### Myth 5: No one can make you feel anything

- The degree to which we are affected and influenced by other people is actually quite terrifying.
- There is evidence that just the very process of thinking things through can turn down the intensity of our emotional responses......**prefrontal cortex(前额皮质) helps us regulate our emotional reactions**. Keeping a cool head, thinking things through, trying to be objective -- all of these things can genuinely help us to some degree.
- We have the tendency to conform instinctively to the roles that others create for us (Stanley Milgram的著名电击实验)
- People are reluctant to recognise how much of their everyday experience 'is determined not by their conscious intentions and deliberate choices, but by mental processed put into motion by their environment'. [John Bargh, Psychologist from Yale]......we may think we're calling the shots, but most of the time we are not even aware of the extent to which we are being unconsciously cued into particular roles by the actions and behaviour of those around us. How we experience the world, and even how we experience ourselves, is largely determined by others.
- Various studies have confirmed that people tend to copy each other's body language, facial expressions, speech patterns and vocal tones. The reason this automatic mimicry is crucial in understanding social influence is because psychologists believe it may be one of the mechanisms that underlie emotional contagion.
- It seems likely that by unconsciously copying the behaviour and micro-expressions of people around us we consequently end up replicating their emotions. In fact, research has established that even feelings like loneliness can be catching.
- It is not only through the subconscious power of imitation that we are exposed to the emotions of those around us. It turns out that we are neurologically configured to connect up with what others around us are experiencing. In recnet years scientist have discovered specialised mirror neurones in the brain that effectively put us into the other person's shoes.
- We should recognise just how vulnerable and open we are to the invisible and unconscious influence of those around us.
- Our spontaneous internal reactions to the people around us and the things that happen to us are an important part of being fully alive.

### Myth 6: Think positive ans be a winner!

- Independent studies have shown that while for non-depressed people positive affirmations do appear to dampen down levels of responsiveness in the amygdala (_effectively the 'fear center' of the brain_), for depressed people the opposite effect is produced: the amygdala becomes more rather than less active while the affirmations are being rehearsed. 
- Whereas positive mood seems to **promote creativity, flexibility, cooperation and reliance on mental shortcuts**, negative mood trigger more attentive, careful thinking, paying greater attention to the external world [Joseph Forgas, professor of social psychology]

> Hui: There is a reason for everything's existence. We need both sides and the key is to keep balance as in a million other situations.

- Depressed people are also better at sequential decision-making. they accept options less readily which led to longer search and better choices. Depression, by fostering greater persistence many improve performance in certain task.

> Hui: I doubt it. 1) how to define better choice? 2) does longer search lead to better choice or increase the likelihood of making better choice? I think the ability of making choice is developed overtime. 3) persistence is personality which is relative stable across time and situation. I can’t imagine depressed people are more persistent or being depressed will make you hold on longer. How they collected the data and do analysis? How they choose samples? Are those samples representative?

### Myth 7: We need to talk......
### Myth 8: Whatever your problem, CBT is the answer
### Myth 9: You can never be too assertive
### Myth 10: Men and women live on different planets
### Myth 11: Your inner child needs a hug
### Myth 12: You can learn to do anything you want
### Myth 13: You'd better get yourself sorted
### Myth 14: You are stronger than you know
### Myth 15: You are a master of the universe!
### Myth 16: There is no failure, only feedback
### Myth 17: It's all your parents' fault
### Myth 18: You can heal your body
### Myth 19: You are in control of your life
### Myth 20: Married bliss: a matter of give and take
### Myth 21: Discover the real you!
### Myth 22: Make every second count
### Myth 23: We must all strive to be happy
## The Optimism Bias [Tali Sharot]

## Art of Thinking Clearly [Rolf Dobelli,清醒思考的艺术]
1. 幸存偏差：由于日常生活中更容易看到成功而非失败，使得人们高估成功的希望（创业）
1. 游泳选手的身材错觉：混淆选择标准与结果（模特因为漂亮才选来拍化妆品广告，而非因为用了这些产品才漂亮）
1. 过度自信效应：1）不存在不够自信效应；2）男性更加严重；3）悲观者只是高估幅度少些。
1. 从众心理
1. 纠缠沉没成本：all pay auction的困局
1. 互惠偏误：互惠古来有之，是出色的生存智慧。没有互惠人类早灭绝了。但注意不要被互惠道德绑架。
1. 确认偏误：所有思维错误之父......过滤与我们观点相矛盾的信息。宗教和哲学信念是杰出的例子。
1. 权威偏误：对权威批判性越强，你就越自由。
1. 对比效应/框架效应/锚定效应：这几个都类似
1. 现成偏误：依据现成的例子来想象世界。某种东西反复出现我们的大脑就很容易重新提取（接受）它，尽管不一定是真的。
1. 事后诸葛亮(Hindsight Bias)
1. 司机的知识：播音员是话筒不是专家。芒格认为知识有两种：1）真知识，来自那些投入大量时间和思考获得知识的人们；2）司机的知识，装的好像知道的人，他们会模仿别人的表演，也可能有动听的声音或具有说服力的形象。但他们传播的知识是空洞的，他们高谈阔论地挥霍华丽词汇。企业越大，人们越期望它的CEO具有表演才能——交际能力。
1. 控制错觉：你对你生活的控制比你以为的要少。(电梯上的安慰按钮。公司温度控制的按钮。)
1. 激励过敏：激励机制能够解释90%的个人或者组织行为。
      1. 一旦有激励加入游戏或改变了激励，人们就会迅速而剧烈地改变自己的行为
      1. 人们是对激励做出反应，而非激励背后的目的（1947悬赏羊皮纸手稿，为了增加数量而将手稿撕碎；19世纪，中国悬赏征购恐龙骨，恐龙骨被敲碎。）
1. 回归均值：避免错误归因，恢复正常可能只是回归均值在起作用
1. 公地悲剧：凡好处归个人而成本由集体承担的地方就潜伏着公地悲剧。在小范围群体里，道德的制裁至今有效，因为人们相互认识，如果有人只考虑自己的好处，滥用公共利益，就会被发觉，并遭到最严厉的惩罚——失去名誉。但在一个匿名社会里道德就没那么管用了。解决方法有两个：1）私有化；2）加强管理。
1. 结果偏误：100万只猴子在股市投机，20年后有1只猴子每次都赚钱，媒体会阐述其“成功原理”。不要完全用结果判断决定，结果差并不意味着决定不对，反之亦然。
1. 选择的悖论：在无限选择的年代，适合自己的局部最优选择更好。
      1. 选择范围太大会导致无所适从
      1. 选择范围太大会导致更糟决定
      1. 选择范围太大会导致不满
1. 讨喜偏误：我们会觉得一个人讨喜，若此人 1）颜值高；2）和我们相似；3）喜欢我们。不要被一时感情冲昏头脑。
1. 禀赋效应：我们对自己拥有的东西估值更高。让我们放弃要比让我们囤积难。这解释了我们为什么会在房子里堆满废物，也说明了为什么邮票、手表或者艺术品收藏者很少交换出售藏品。禀赋效应不仅神话了我们已有的财产，甚至神话了可能会拥有的财产。在拍卖中有“赢家的诅咒”：拍卖的赢家反而是经济上的输家，因为他出价过高。......结论：勿过于执著于某物，理解来去无常。

      > Hui: 这让我想起focusing illusion

1. 奇迹：小概率事件可以发生，不要过度解释。
1. 团体迷思：一群智慧的人做出愚蠢的决定，因为每个人都误以为自己的意见是正确的共识，从而作出他们每个人在正常情况下都会拒绝的决定。这是从众心理的一种特殊情况。（Pig bay evation）
1. 忽视概率偏误：我们对一件事的强度做出反应而非概率，我们缺少对概率的直觉理解。（一定会遭受电击，和有50%／20%／10%／5%的概率会遭到电击，两种情况下受试者一样紧张。预期电击强度增大时，两组紧张感同时增大。概率降为0才会有不同。）我们不能区分理解风险。
1. 零风险偏误：我们只信任0风险。我们常愿意投资过多的钱，就为了彻底消除微小的剩余风险。（俄罗斯轮盘赌：共可装6发子弹，假设装有4发，发愿意付多少钱拿走2发？假设装有2发，你愿意付多少钱将这2发都拿走？）......结论：学会怀着“没有什么是绝对安全的”想法生活——无论你的积蓄，健康，婚姻，友谊。满足于至少有东西让你保持相对稳定并体验自身快乐。研究表明，无论是中百万彩票还是半身瘫痪都不会长期改变你的满意度。不管发生什么，快乐的人照样快乐，不快乐的人总是不快乐。
1. 稀少性谬误：物以稀为贵
1. 忽视基本概率：创业的成功率就是那么低，无论你多努力，多聪明，你都更可能失败。意识到基本概率。
1. 赌徒谬误：连续出现红球，下一个更可能是黑球么？注意是否是独立事件。现实生活中的事件大多数有相互联系。

       > Hui:总觉得这个和均值回归有冲突啊
  
1. 锚定效应（Anchor effect）

       > Hui: 这个简直家喻户晓。之后在Predictable Irrational会讲到。
       
1. 归纳法（induction）：generalize results from small sample.我们自欺欺人。很少生病的人觉得自己不会死。连续几个季度利润增长CEO觉得自己不可缺少。人类一直成功因此我们可以征服未来的挑战（只有那些幸存到现在的物种才能这么说。）**以我们存在的事实来说明将来我们也会存在，是一个严重的思维错误——估计是最严重的**。 
1. 损失规避：人们害怕失去某种东西的想法要比获得某种同等价值的东西的想法强烈。我们无法改变：恶比善更有影响力。我们对不利的东西反应要比对有利东西反应敏感。一张凶恶的脸要比一张友善的脸更容易引起我们注意。**恶行要比善行更永久地留存在我们的记忆里。当然也有例外：事关我们自己的时候。**
1. 社会性倦怠：责任扩散，个人效率无法直接看到，导致尸位素餐，群体效率下降（都指望别人嘛： ））。这是一种我们让自己亏欠所有人的欺骗形式。这一欺骗大多不是故意的，而是不知不觉的发生的。为什么不完全懈怠？因为0效率会引起注意——继而会带来后果，如被逐出群体或损坏名誉，我们能细腻地感觉到，懈怠到什么程度不会被看出来。出于同样的原因，团队有甘冒比个人更大风险的倾向。人们称这一效应为风险分摊。可以通过尽量彰显个人效率来缓和团队的弊病。
1. 指数增长
1. 赢家的诅咒：拍卖的赢家大多是事实上的输家。1）一种货物的真实价值是不确定的。出价方越多，报价过高的概率就越大。2）我们想排挤竞争对手。
1. 基本特征谬误：系统性地高估人的影响，在解释某些东西时低估情境因素。领导才能对经济成功的影响程度要远远小于普遍的经济形势和行业的影响力。在一个存在危机的行业里，首席执行官们常被撤换。.....极度关注他人源自我们过去的进化史，隶属于一个群体是生存所必需的，被排斥意味着死亡。繁殖、自卫和狩猎，大多是个体做不到的。我们需要别人协助。特立独行的人早就从基因池里消失了。因此我们才会这样过度地关注人。我们将90%的精力都用来关注人，只用10%的精力关注情境。不管戏剧多么让我们着迷，舞台上的人绝非孤立的，他们的表演离不开一个个情境。你若真想理解正在表演的戏剧，就请你不要只注重表演者，而是多关注他们的表演或舞蹈。
1. 错误归因
1. 光环效应
1. 替代途径：风险从来不是一眼就能看到的。因此，请你时刻考虑你有什么样的替代途径。比起你通过无惊险的平凡途径获得的成功，别拿通过冒险的替代途径获得的成功太当真。蒙田怎么说来着：“我的生命充满不幸——这些不幸大多没有发生。”
1. 预测错觉：什么可以预测，什么不可以预测？一件事情越复杂，时间跨度越长，其未来的发展变化就越多。
1. 关联谬误：大脑的系统1会自动把线索连起来编故事。
1. 框架效应：同样的内容，换个不同的说法，效果不同。
1. 行动偏误：为什么不行动光等待是中痛苦？源自远古基因。在一个狩猎采野果的环境中，行动比思考价值大得多。在古时，闪电式反应关乎生死存亡，思考则可能会致命。如果情况不明，不要采取任何行动，直到你能更好地分析形势，你要克制自己。
1. 不作为偏误：其出现在无论放弃还是行动都会带来损害地地方。在这种情况下大多数人都会选择放弃，因为这样引起地损害主观看来更无害。“如果你不是答案地一部分，就是问题地一部分[1968欧洲学生运动口号]”
1. 自利偏误：成功归于自己，失败归于外因。
1. 享乐适应：
      1. 请避免很长时间也不会习惯地负面效应，如交通，噪音，慢性疲劳等。
      1. 对物质的东西只期待短期效果，例如汽车，房屋，分红等。
      1. 持续正面效应主要与你如何利用时间有关。设法让自己得到尽可能多的自由时间和自主权。请你做最爱做的事情——哪怕你要付出部分收入。请为友谊投资。
1. 自我选择偏误：当我们本身时样品的一部分时，我们必须注意，不要掉进一种以自我选择偏误著称的思维错误陷阱中。
1. 联想偏误：影响我们决定的质量。我们倾向于不喜欢送坏消息的人（Shoot the Messenger Syndrome）
1. 新手的运气：如果你长期比其他人成功，你可以认为自己的才华可能起作用，但绝不能过于自信、自满。参与的人越多，出于纯粹运气长期成功的概率越大，也许你就是这个某人。
1. 认知失调(Cognitive Dissonance)：酸狐狸
1. 双曲贴现：一个决定离现在越近，我们的“情感利息”就越多。这是及时享乐对我们的控制，我们过去动物性的残留。动物不愿意为在将来得到更多的奖励而放弃今天的奖励。

> 在群体里容易按照他人的想法生活，在孤独中容易按照自己的想法生活，但值得记住的只是那些在群体中保持独立的人。—— 爱默生


## Thinking Fast and Slow [Daniel Kahneman]
## Predictable Irrational

### Goal: what makes you and people around you tick?

behavior economics, judgment and decision making (JDM)
Generalized Axiom of Revealed Preference (GARF)

We are irrational
Our irrationality is predictable

- The fallacy of supply and demand
James Assael, Salvador Assael (peark king, James' son), black pearl from black-lipped oysters, put them in the window of Harry Winston's store on Fifth Avenue, Tahitian black pearls glowed

> Mark Twain in Tom Sawyer: "Tom had discovered a great law of human action, namely, that in order to make a man covet a thing, it is only necessary to make the thing difficult to attain."

Anchor effect: last two digits of social security number, how much would you pay for the product?

Assael anchored his pearls to the finest gems in the world and the prices followed forever

## Mind Control 
### Ch 1 赢家不会告诉你的
- 保证自己成功的工具并不是执行力，而是明智的态度，冷静的判断和别具一格的思维
- 把你看到的人变成“你的人”，让更多的人想成为“你的人”， 这就是优秀领导者的魅力
- “成功可以复制”是谎言
- 表演的是狗熊，收钱的是驯兽师。成为“善舞的狗熊”是一个悲剧的目标
- 黑色人种为何散漫，漠视规则，难以形成高度的组织和纪律性？
- 白人基因有哪些与众不同的优点，又有哪些明显弱于东亚黄色人种的缺陷，从而导致了基督教文明与儒家文明的区别？
- 基因在很大程度上决定一个人的抗洗脑能力有致命影响。相较而言，华人总是很难被洗脑，他们既依赖权威，同时又不相信权力，也从不迷信鬼神的力量，并对任何单一和极端的“信仰”敬而远之。

     > Hui: I totally can't buy this point......

- 金钱总是在底层群体的手中进进出出，而永远在上层少数人的口袋里驻扎。富人的智慧：
      1. 他们不相信任何已经成功的人，从不迷信和追随某种经验。
      1. 从不制定宏观计划，而是注重于沿着趋势去推动事情。
      1. 他们深知金钱的用途，在滚雪球的过程中，懂得集中力量、聚成一团和重点使用的价值，不会将钱分散开来，而是能够抓住孤注一掷的时机。
- 洗脑金字塔： 1）洗脑源；2）传教士；3）中产；4）洗脑受体。

     > Hui: 信息!= 真实信息  <----- 阶层，信息源，目的，判断力

- 整部人类历史的发展背后，这一洗脑原则始终被牢固地贯彻下来，每一种文明都是如此，这就是世界各地优秀文化思想全部诞生在公元前，之后就一直裹足不前的原因。

     > Hui: “各地优秀文化思想都诞生在公元前”这个观点有趣，仔细想想还真是那么一回事......>_<

- 一个人只有站得高才能看得远，与他是否足够努力并没有必然关系。时间未必可以换来金钱。

> Hui: 上层能够获取-----> (信息，资源，人脉)------>通过资本运作致富

- 专注于提升自己的生活而不是去过量入为出的日子。
- 赢家法则 （Hui: 看到这样的标题感觉是传销，之前都说了成功不可复制不是么？怎么又来这么多法则？）
     - **在改变规则前遵循规则，重要的是前者**
     - 不要重复任何一件事情，即使是必要的（Hui: 太武断了）
     - **主动收集信息，尽可能去的一手资料，而非经由他人** （Hui: 有时间精力是该尽量要一手资料的）
     - **简练，直接，命中要害**
     - 结盟而非敌对
     - 看到问题是开始，解决问题是目的
     - 善于谈判，和每个人保持互相理解的心态
     - **如果一开始就看到的方案，自动跨越所有步骤**

- 弱者（没有精气神，不敢竞争，羞于展示才华）  
强者（耐心，恒心，勇气）
- 人们进行判断的原则常带有浓厚主观色彩

### Ch2 苹果的滋味
- 任何行为和思维，通过不断重复都会得到加强，并最终成为本能。
- 每件事情都有联系，把它们联系起来，就成了一张符合逻辑的大网
- 打造一个让人深度信任的平台环境，对方深信在你这儿他可以赢（Hui: 如何做？）


# Society and Culture  

## Much Depends on Dinner [Margaret Visser]

### Introduction
- We prefer, as De Quincey's essay says, "to throw the grace of intellectual enjoyment over an animal necessity." （正如De Quincey在文章中说的，我们喜欢“用优雅的精神享受来掩盖动物性的需要”。）
- Again, we should be aware that our meal is almost totally **female in connotation**. _Corn_ is the American Indian "mother and nourisher"; _chicken_ (pale meat, no red blood, and little fat in evidence) is for us a typically "female" choice; _rice_, a delicate grain-----especially when it is "fluffy", as we like it-----white like chicken, and in its **mythical origins** a girl-child; _lettuce_ is light and unfattening, but also cold, milky, and female; _lemons_ nippled, _olive oil_ virgin, _ice cream_ cold milky, and served in definitely womanly, rounded shapes; _salt_ is the on exception, but even it is neuter and not masculine; _butter_ from cream is again female.

### Corn
- 玉米片(Corn Flakes)
凯洛格所用的**“谷物回火”**方法在**1894**年取得专利。(The **Kellogg** "grain-tempering" process was patented in 1894.)
－ 玉米和遗传学(Corn and Genetics)
在美洲殖民地无所不在的玉米，除了食用之外又发展出上千种用途，其中一个用途就是用玉米穗轴制成的烟斗。(The ubiquity of the corn plant in **Colonial America** had made it standard material for a thousand uses which had nothing to do with food. One devive was the corncob smoking pipe.)
- 玉米植株兼具雄性（穗）与雌性（须）两种性别，杂交玉米通过摘除自身的穗来完成，这样以来，玉米植株就不会自身授粉，而是必须接受来自其它植株的花粉。......通过受制遗传，培育出雄花不育的植株。(A corn plant is both male (its tassels) and female (its silks). Hybrid corn seed is to bear the grain, so that the plant cannot seed itself but will receive pollen from the other inbred parent chosen to be planted in the same field......by genetic manipulation, to produce no pollen.)
- 同一性是一个现代社会特有的诅咒，它伪装着自己，以多样化的形式装在超市的罐头里，盒子里，瓶子里和纸板箱中。每一件摆在架子上的东西里都含有玉米，因此我们依赖着玉米，玉米也依赖着我们。我们自己证明出来的无能为力，却让我们承担起越来越多不可逃避的责任。(Uniformity, disguise itself as it may behind the multiplicity of cans, boxes, bottles, and cartons in our supermarkets, is a peculiarly modern curse. Everything on the shelves contains corn. We therefore depend on corn. But corn depends increasingly, because of our wanton（荒唐的） wastefulness, on us. Our own demonstrations of our incapacity to manage have placed us more exclusively and inescapably in charge.)

### Salt

- 盐税，中国从公元前7世纪开始由政府垄断了盐。(China had a salt monopoly from the 7th century BC. Salt was also one of the first commodities to be taxed. "The art of taxation consists of plucking the goose so as to obtain the most feathers with the least hissing.)
- 1825年，经过了400年的怨恨与诅咒，英国废除了盐税，是第一个废除盐税的国家。(In 1825, after four hundred years of resentment, England abolished her salt tax. She was the first country to do so.)
- 为夺回印度的盐并在不加税的情况下进行买卖，印度人民的非暴力不合作运动开始了。(Non-violent activities undertook to get India's salt and sell it free of tax.) 
- 盐，明亮，干燥，愉快，强悍，在许多种语言中，都是聪明与睿智的同义词。(Salt, bright, dry, titillating, and dynamic, is synonymous in several languages with wit and wisdom.)

### Ice-cream
- 至少在1100BC，中国人就知道如何在地下建造冰库。

> Hui: 有种说法是，唐朝的《酉阳杂俎（yǒu yáng zá zǔ）》[是笔记小说集]里头，已经提到过冰与奶制品混一的玩意，叫做“酪饮”。宋朝时，大家也习惯类似东西叫冰酪，可能那就是冰淇淋的雏形。但法国人相信，冰淇淋是美第奇嫁到法国之后，才真正进入文明世界的——那就天晓得了。[“美第奇家族”（Medici Family）是佛罗伦萨13世纪至17世纪时期在欧洲拥有强大势力的名门望族。Maria de' Medici于1600年嫁给亨利四世，成为其第二任妻子，法国王后，路易十三的母亲。她是意大利豪门美第奇家族的重要成员。]

- 第一个影响深远并且享有声望(influential and lasting fame)的咖啡馆(Cafe)，是巴黎的Cafe Procope。Francesco Procopio dei Coltelli在1686年开办了这座咖啡馆，他是意大利人(Italian)，可能经由弗洛伦萨(Florence)从西西里岛(Sicily)而来。
- The first automatic cane-rolling machine（蛋筒制造机）was invented in 1909.
- 1932年，冰激凌工业进入岛一个全新的阶段(entirely new phase)，这是Clarence W. Vogt 发明了连续冰激凌冷冻制造机(continuous ice-cream freezer)。

### Sugar (from an article)

东汉明帝驾崩，马皇后成了马太后，大臣疑心她要专权，太后就说，咱以后，含饴弄孙——含着麦芽糖逗逗孙子，这就能过日子了。罗马帝国时期，甜品单里大多是新鲜或干透的水果，以此取甜。  

用蔗糖最早的，应该是印度人。公元前三世纪，亚历山大东征，在印度发现有人嚼甘蔗取甜味，觉得有趣，便想法子移种。蔗糖提取不易，所以人类历史上大多数时候，砂糖的供应不顺畅。甜味曾经是个政治问题。跟英国人有关的糖危机，发生过两次。一次是19世纪初，英国人跟拿破仑打仗，拿破仑打不过英吉利海峡，便搞经济封锁，英国人一生气，也不给欧洲大陆供蔗糖。拿破仑御下的大陆诸国要哭了：一口甜的都吃不上！德国人这时跳出来：咱有甜菜，可以榨糖，让蔗糖去死吧！结果德国经济靠此崛起，实在是意料之外。另一次是20世纪初，《泰晤士报》连篇累牍，说只有下等阶级的人才爱吃甜喝甜，嗜糖如命。上流社会都要修身养性，减少食物含糖量还来不及呢。结果英国人对茶里放糖，依然故我。到二战时，人民需要营养和热量，支持抗击纳粹事业，实行配给制，糖不够用，怎么办？答：往茶里加牛奶，“多加些牛奶，茶就甜了。”

葡萄酒发酵，酒精度和糖分此消彼长，所以爱喝偏甜葡萄酒的，就会被资深好酒者小看。南欧惯例，像葡萄牙、西班牙和南法酿葡萄酒，都喜欢加酒精强化，提前终止发酵，导致葡萄酒甜浓醉人。但这种喝法，法国北部的人就不大喜欢。德国人喝啤酒，嫌麦酒太甜，加了啤酒花，得了其中的清爽苦味才过瘾，反过来还要嘲笑：波兰这群胖子，就是爱喝甜烧酒，个个都是大冬天长个酒糟鼻子！

如此，口味甜不甜，在欧洲像个阶级问题。

福塞尔(Paul Fussell, American cultural and literary historian, author and university professor)《格调(Class)》里认为，现代社会，下等人才会迷恋甜味。上流社会也因此摇旗鼓吹，认为懂得品茶与咖啡的苦味，才能谏果回甘，体会到深层的味道云云……大概可以这么说：上等人觉得，甜味经常显得女性化、脆弱、下等、世俗、不够高雅，能尝得苦味才显得品味非凡、耐得住寂寞等等，但抛去一切形而上的想象，我们普通人类本性的DNA里，还就是喜欢甜的东西。

> Hui: 《格调》是一本精确而刺痛人的社会等级指南。等级是什么？它不是你的职业，不是你居住的地方，不是你的餐桌举止，不是你有多少钱或者你能挣多少钱。**等级是一系列细微事物的组合**，你很难说清楚。正是这些细微的品质确立了你在这个世界上的位置。作者通过敏锐的观察、独特的视角、鞭辟入里的分析和机智幽默的文笔，把美国社会中的社会等级现象和三六九等人的品味做了细致入微的对比。 


## The European Coffeehouse Culture [咖啡馆里的欧洲文化，克劳士.提勒多曼]

- 根据一个有趣而且听起来可信的说法，咖啡不是由人，而是由动物发现的。大概在500年前，衣索比亚的牧羊人注意到他们的山羊吃了灌木丛中一种红色的莓子之后，突然兴奋的跳起来；牧羊人也好奇地尝尝这种看起来像樱桃的果子，结果也感受到类似的兴奋感。于是咖啡在世界各地的流传便开始了。

### Venice [威尼斯]

- 弗洛里安咖啡馆：19世纪巴尔扎克用文字表达出他对弗洛里安咖啡馆的偏好

### Zurich [苏黎世]
欧笛翁咖啡馆

### Vienna [维也纳]
- 维也纳的咖啡馆是咖啡馆中**独一无二**的......其独特性就如同匈牙利骑兵有其无法模仿的特色一样。[奥地利作家Johann Braun Von Braunthal]
- 据说维也纳在**1684**年拥有第一家咖啡馆。
- 在维也纳最早的几家咖啡馆中，**塔罗纳咖啡馆(Cafe Tarone)** 最常出现在人们话题中，它由烈酒商Johann Jacob Tarone于**1784**年成立。
- 格林史戴德咖啡馆(Hugo von Hofmannsthal)

### Hungray [匈牙利]
- 布达佩斯的 Cafe Pilvax  
诗人Sandor Petofi，尝试衔接存在于高尚文学与普通百姓之间的鸿沟，他将许多民间传说及神话写成诗句，这些诗句一方面保持其艺术本质，另一方面也十分浅显易懂。
- Cafe New York  
1894, 坐落于Erzsebet Korut 街的新巴洛克式咖啡馆
- Roland Mischkl: "大部分的侍者都是有美丽外表的女性，她们穿着可爱的围裙，白色或蓝色，及踝的绑带高筒鞋，上了浆的衬衣及深色短裙。那种装扮引起的性感遐想，虽然没有科学解释，却人人都能感受得到。安详闲散的气氛似乎能让人的性感遐想完全释放出来。"

### Germany [德国]
- 狂想咖啡馆(Cafe Grosenwahn)：柏林艺术家聚会的主要地方，主人Rocco, 1914.7第一次世界大战
- 罗曼咖啡馆(Das Romanische Cafe): 主人Karl Fiering， 1916年创立
- 若要以最优雅的方式喝咖啡，在柏林就该造访温特丹林登大道上的Hotel Adlon，这家饭店是招待国宾及外交官员的所在，也是许多国际知名的经济，科学及文化界名人的住所。

### Czech Republic [捷克]
- 在布拉格，饮用咖啡从18世纪初起形成为一种时兴的习惯。1714，Johannes Diodato在哈尔广场(Haarmarkt)开了维也纳第一家咖啡馆，卡维纳咖啡馆(Kavarna)。咖啡馆成为具激发性的艺术家聚会所的全盛时期是20世纪初的事。即使时光流逝，其中有三家咖啡馆至今仍保持它的音乐盛名：

     1. 联合咖啡馆(Cafe Union)：捷克艺术家在此聚会，佩斯提那街(Na Perstyne)，Jaroslav Hasek《好兵帅克》的作者
     1. 雅可咖啡馆(Cafe Arco)
     1. 斯拉维亚咖啡馆(Cafe Slavia)

- “巴黎有它的丁香园，园亭咖啡馆(Cafe La Rotonde)；柏林有它的狂想咖啡馆，而布拉格则有它的联合咖啡馆”[Karel Capek]

### Rome [罗马]
- 希腊人咖啡馆(Antico Cafe Creco)
    - 门德尔松(Felix Mendelssolm)
    - 叔本华(Schopenhauer)
         - 《意志和表象的世界》：“这是一本完全崭新的哲学系统，拥有极高度的思想连结，而这种观点尚未在人类的头脑中出现过......这本书将会成为日后千百本书的资料来源，也将成为许多创作的动机。”
         - "所有东西都是不幸福的"
         - "即使有时候我们真正面临幸福，我们也不会觉察，而让这一切就这样轻易，温柔地与我们擦身而过；一直到幸福不再，空虚的感觉凸显消逝的幸福时，我们才会发现，我们把一切都搞砸了，最后只留下深深的追悔。"
         - "博学多闻的人是那些学了很多东西的人；而天才可以让人类学到他们到现在都还不知道的事。"
    - 卡尔.维特(Karl Witte)，哥廷根，停留罗马期间和叔本华一样是希腊人咖啡馆的常客。十岁时进入大学研读数学和法律，十六岁取得博士学位，当时政府批准乐一项奖学金给这位天赋异禀的年轻人。
    - 也有法国和英国的艺术家造访这家咖啡馆，英国的拜伦，雪莱，济慈(A thing of beauty is a joy forever)

### France [法国]

# Novels and Plays 
## Slowness [慢，Milan Kundera]

> Hui: Milan Kundera is my favorite novelist!

- The source of  fear is in the future, and a person freed of the future has nothing to fear.</li>
- A person with nothing to do is frustrated, bored, is constantly searching for the activity he lacks.
- In such a world, where everything gets told, the weapon that is both most readily available and most deadly is disclosure.
- Nothing in this novel stays a secret exclusive to two persons; everyone seems to live inside an enormous resonating seashell where every whispered word reverberates, swells, into multiple and unending echoes. When I was small, people would tell me that if I set a shell against my ear I would hear the immemorial murmur of the sea.
- Has mankind always lived inside such a resonating shell, without realizing it?
- As is often the case with glory, his was instigated by a defeat.
- And indeed, I wondered, what did become of the kiss that Sublime Planetary Historic News Event  had planted on his brow?
- This is where the courtiers of the News Event make their mistake. They don't know that the situations history stages are floodlit only for the first first few minutes. No event remains news over its whole duration, merely for a quite brief span of time, at the very beginning, The dying children of Somalia whom millions of spectators used to watch avidly, aren't they dying anymore? What has become of them? Does Somalia still exist? And in fact did it ever exist? Could it be only the name of a mirage?
- The way contemporary history is told is like a huge concert where they present all of Beethoven's one hundred thirty-eight opuses one after the other, but actually play just  the first note of each piece would be played, thus one hundred third-eight notes for the whole concert, presented as one continuous melody. And in twenty years, the whole of Beethoven's music would be summed up in a single very long buzzing tone, like the endless sound he heard the first of his deafness.

## Laughable loves [好笑的爱，Milan Kundera]

- She was lounging almost naked on my couch occupying herself with an examination of the ceiling.
- An ugly woman hopes to gain something from the luster of her pretty friend; a pretty woman for her part, hopes that she will stand out more lustrously against the background of the ugly woman. [丑女人往往希望借助她漂亮女友的光彩，而那个漂亮的朋友则希望在丑陋的对照下放射出更艳丽的光彩。]

      > Hui:  想起《清醒思考的艺术》中说的对比效应，这样看来，丑女人的策略不对啊......和漂亮朋友在一起只会显得更丑不是么......

- At birth every human being received one out of the millions of available bodies, as one would receive an allotted room out of the millions of rooms in an enormous hotel; that consequently, the body was fortuitous and impersonal, only a ready-made, borrowed thing. [任何一个人在生下来时，都在几百万可供使用的肉体中获得了一个肉体，就仿佛人们分配给了她一套住所，它就像一座巨大的大厦中其他几百万套住所一样；她对自己说，肉体是一种纯属偶然的非个体的东西；只不过是一件借用的和现成的物品。]
- Of course it was a quite naive desire, but there it was childish desires withstand all the snares of the adult mind and often survive into ripe old age. And this childish desire quickly took advantage of the opportunity to embody itself in the proffered role. [这无疑是一个相当幼稚的愿望，但这有什么办法：童稚的渴望摆脱了成人精神的一切樊笼，继续存在下去，有时候甚至在遥远的老年期依然还要冒出来。]
- The more the girl withdrew from him psychically, the more he longed for her physically; the alienation of her soul drew attention to her body. [她在道德上越是于他陌生，他就越是在肉体上渴望她；灵魂的陌生使她作为女人的肉体更为奇特。]

      > Hui:如何概括这种心理？贱！

- The alien life in which she had become involved was a life without shame, without biographical specifications, without past or future, without obligations; it was a life that was extraordinary free. The girl, as a hitchhiker, could do anything: everything was permitted to her; she could say, do, and feel whatever she liked. 
- It had always seemed to him that her inward nature was real only within the bounds of fidelity and purity, and that beyond these bounds it simply didn't exist.
- And it was futile to evoke good sense and warn her dazed soul that she must keep her  distance from the game and not take it seriously. Just because it was only a game her soul was not afraid, didn't oppose the game, and narcotically sank deeper into it.
- These two images showing through each other were telling him that everything was in the girl, that her soul was terrifyingly amorphous, that it held faithfulness and unfaithfulness, treachery and innocence, flirtatiousness and chastity. This disorderly jumble seemed disgusting to him, like the variety to be found in a  pile of garbage. 
- **Perhaps I want to resist necessity. To trip up causality. To throw off the predictability of the world's course through the whimsicality of caprice.**
- How can you be a conqueror in a domain where no one refused you, where everything is possible and everything is permitted?
- In them he saw the callousness of  aging men and women, the cruelty of their mature years, which rose before his youth like a hostile barrier.
- It was not a question of suicide but of a demonstration of suicide set up in such a way that a disaster would not occur.
- She saw herself without her own head. So to herself she was completely beautiful.
- He was seeking a comforting embrace, never-ending and vast, which would redeem him from the infernal relativity of the freshly discovered world.
- Only at the last moment, when they had almost passed each other, that smile rang a bell in his memory and snapped him out of his drowsy state.
- Women became for him the one legitimate criterion of life's density.
- He said to himself that there was a curious malice in the fact that he had met this woman, with whom he'd been head over heels in love and whom in those days he'd let escape, precisely when he found himself in this state of mind and at a time when it was no longer possible to rectify anything
- Havel, beneath the many glances, felt how once more he was regaining his lost visibility.
- The interlocking conjunction of all these forces eventually dumped him (as a crane drops a sack onto a truck) from secondary school into teacher's college...... He understood, however, that his occupation would be among the fortuitous aspects of his life.
- But this is the way life goes: a man imagines that he is playing his role in a particular play, and does not suspect that in the meantime they have changed the scenery without his noticing and he unknowingly finds himself in the middle of a rather different performance.
- Now, however, the unpremeditated snare of false news caused a split in the coherence of her being and it seemed to Edward that her convictions were in fact only something extraneous to her fate, in fact only something extraneous to her body; he saw her as an accidental conjunction of a body, thoughts, and a life's course, an inorganic conjunction, arbitrary and unstable. He visualized Alice and he saw her body separately from her thoughts; he liked this body but the thoughts struck him as ridiculous, and together they did not form a whole being; he saw her as an ink line spreading on blotting paper, without contours without shape.
- If you told him the whole truth and nothing but the truth, only what you really thought, you would enter into a serious conversation with a madman and you yourself would become mad. And it is the same way with the world that surrounds us. If I obstinately told the truth to its face, it would mean that I was taking it seriously. And to take seriously something so unserious means to lose all one's own seriousness.
- It occurred to him that these were signs devoid of meaning, currency without funds, weights made of paper.
- And that is why Edward longed for God, for God alone is relieved of the distracting obligation of (he himself, unique and nonexistent) the essential opposite of this unessential (but so much more existent) world.

## The Lover [情人, Marguerite Duras]

> Hui: Finished this book in 2010.6. Marguerite Duras is a controversial writer:  cold, cranky and so egocentric. You may not like Marguerite Duras herself, but you can't reject her words: sharp and bold. She dares to say anything. You can let her die but can't make her shut up. She persist in writing all her life. If she wants to do something, she will do it and that's the woman. She said: "If I were not a writer, I would be a hooker." But I think if she hadn't been a writer, she would suicide.   
When reading her words, your heart may skip a beat from time to time. As I said before. "being happy" is like "playing piano", it's a skill rather than human nature. You need to learn and practice. However, she doesn't own the skill. She lost in her world and her desperation. She was brave and honest. She talked about naked sex, desperation, fornication without disguise. She is not my favorite. BTW, I am so sorry about her Chinese lover. And I have to state that not every Chinese is like him. 

- Dreamer

She is such a dreamer that there is noway to wake her up. See the beginning and ending of the novel:

> Beginning: One day, I was already old, in the entrance of a public place a man came up to me, He introduced himself and said, "I've known you for years. Everyone says you were beautiful when you were young, but I want to tell you I think you're more beautiful now than then. Rather than your face as a young woman, I prefer your face as it is now. Ravaged.

> Ending: And then he told her. Told her that it was as before, that he still loved her, he could never stop loving her, that he'd love her until death.

The paradox lies between her belief in love and her fear to break it. Duras was highly influenced by the difficult life that her family experienced during the period in Indochina. There was no love in the family and she said:

> It's a family of stone, petrified so deeply it's impenetrable. Every day we try to kill one another, to kill...... the face that all three of us are our mother's children of a candid creature murdered by society. We're on the side of the society which has reduced her to despair. Because of what's been done to our mother, so amiable, so trusting, we hate life, we hate ourselves.

That's why she was eager for love . She kept the love with her Chinese lover by ending it. So she could tell herself: "he loves me forever". It was over because she had to leave but not the problem of the love itself. However, if she hadn't left, their love might still be over one day but because he wouldn't love her anymore which was unacceptable. I think she knew it. That's a very good trick. She left when they still loved each other so their love was not destroyed and couldn't be.  Moreover, for her Chinese lover and his new wife, she assured:

> It must have been a long time before he was able to be with her, to give her the hair to their fortunes. The memory of the little white girl must have been there, lying there, the body, across the bed. For a long time she must have remained the queen of his desire, his personal link with emotion, with the immensity of tenderness, the dark and terrible depths of the flesh.

Such a dreamer! He might forget her not long after her leave and started a new life. Who knows? Similarly, she also considered that her little brother's death made him immortality.

- Distance

She kept a distance to world around. There were two things kept the distance not too big so that make her alive: writing and drinking. She said: "I drink because I know God does not exist".  I like her courage to face her life and say the truth in humanity out.

- More quotations

> Departures. They are always the same.

> The thing that's between us is fascination, and the fascination resides in our being alike. Whether you're a man or a woman, the fascination resides in finding out that we're alike.


## Plays of Marguerite Duras

> Hui:Here are some quotations of her plays. I won't read anymore works of this writer. 

- It's agony. Being so near to you and yet so far.
- It's a gram-phone. I'm like that. I keep my word. I hope you'll get to know me.
- I mean nothing to you, less than nothing.
- Another time, I took Mr. Jo's presents, the blue dress, the compact, the nail polish, and threw them in the river. That meant there was nothing left to sell.
- Cleaving the sea with her body. Disappearing in an eddy. The water closed up over her. 
- Cries out that her skin is burning, scorching against his.
- A love...A love belonging to every moment without a past, without a future. Changeless. A crime.
- Because...I forgot what I'm weeping for.
- She belongs to whoever wants her. Gives her to whoever will have her.

## L'Assommoir [小酒店，Émile Zola]

- 她头越来越低，双手捂住了双眼，仿佛要让自己消失在遗忘的黑暗之中。
- 那些留下来的则伸长脖子，眼神中露出残忍的凶光。
- 酒足饭饱，张开双手拍着大腿，安详缓步地走进嘈杂拥挤的人流中去了。
- 热尔维斯渐渐感到累了，头伏在枕头上，微笑着发呆；她看得见，听得见，但却无力做动作或开口：她觉得似乎自己已经死去，十分适意的死去，看到别人活着，她感到欣慰。
- 当她梦想到她的店子时，常常面对时钟发呆，眼睛死盯着时针转动，恍若在等待着某一个特殊隆重的时刻来临，以便最后下决心。
- 她只好躲躲闪闪，仿佛一个大人做了孩子气的事而见不得人。
- 她流落到街头时的理想：工作，有面包吃，有一个自己的小窝，抚养孩子们，不挨男人打，能死在自己的床上。
- 她眼前始终浮现着那个四岁女孩的目光，那么庄重，那样勇敢，只有一个成年女人才会有的目光。
- 男人们很喜欢捏她，因为他们可以捏遍她的全身而不碰到骨头。
- 他们走了进去，要喝一杯李子酒，惟一目的是在一起饮酒，庆贺一下改邪归正的决心。
- 她的神情十分专注，那双邪气十足的孩子的大眼睛，因被淫荡的好奇心驱使而闪闪发光。
- 他们把她当作蜡烛，从两头点燃......他所受的教育像不爱干净的人们穿着一件下面带有污垢的白衬衫。
- 起初他们转来转去，找不到东西，犹如玩乐过度的第二天疲惫不堪。
- 当一个人不再哭泣时，悲伤即转化为厌烦。
- 库波躺下了，他说不是为了睡觉，而是为了思考。

> Hui: 哈哈，这个经典！

- 拉丽仅仅保持着沉默的目光，一双黑色顺从的大眼睛，让人感到眼底深处蕴含无穷无尽的悲哀和痛苦。她始终默默无语，只有一双黑色的大眼睛睁得很大。
- 习惯如同别的东西一样可以消磨正直感。
- 当他站在窗前时，人们可以透过他得身子骨见到阳光，他实在是太瘦了。
- 她的死正是因为她小小年纪便有了一个真正的母亲的理智，她的心胸还太嫩，太狭小，容不下这么宽厚的母爱。
- 当然，这是不干净的，但是这时干净与不干净在她的脑子里混淆了，人在饿得要死得时候不会谈这么多得哲理，只会吃能到手的面包。
- 她看着他，仿佛要寻找那条她抛弃过尊严的沟渠。
- 这是一场真正的风雪，在广阔无垠的天空中，细雪飞旋着，仿佛从天空的四个角同时吹来。
- 她停下来，踌躇不定，转回头，猜想着在这雪帘子后有开阔的大街，有一排排望不到头的煤气路灯。还有沉睡的巴黎无限的黑暗与荒凉。

# History                   
# Business & Economics 
## The Wealth of Nations [Adam Smith]
### Of the Causes of Improvement in the productive Powers of Labour, and of the Order according to which its Produce is naturally distributed among the different Ranks of the People
#### Of the Division of Labour

The author discussed the cause and effects of division of labour.

- The division of labour arises from a propensity in human nature to exchange [分工不是人类智慧的结晶，是因为我们需要互相帮忙，人类这种需要交换的趋势促成了分工的产生。]
- The division of labour (not natural differences) gives rise to differences of talent. [分工导致了人们在不同事业不同领域表现各种才能，而不是天赋的差异导致分工]

#### Of the Principle which gives Occasion to the Division of Labour [论分工如何受到市场范围的限制]

- 分工的程度会被当时的交换能力限制住，而分工又起因于交换能力，当然这个范围限制决定了分工的范围。市场小：不鼓励专一职业。因为人们没有能力把自己消费不了的劳动产品中的剩余部分哪去交换别人的剩余物品。

## Principles of Economics [Alfred Marshall]
### Introduction

- **Political Economy** or **Economics** is a study of mankind in the ordinary business of life......it is on the one side a study of wealth; and on the other and more important side, a part of the study of man.......two great forming agencies of the world's history have been _religious_ and _economic_.

> Hui: I agree. Religion and economy set the frame.

### The substance of economics
- **Economics** is a study of men as they live and move and think in the ordinary business of life. But it concerns itself chiefly with those motives which affect, most powerfully and most steadily man's conduct in the business part of his life......the steadiest motive to ordinary business work is the desire for the pay which is the material reward of work. 


# Art     

# Proses, Essays and Poems

## The Thoughts of An Idle Fellow

- There are plenty of lazy people and plenty of slow-coaches, but a genuine idler is a rarity. He is not a man who slouches about with his hands in his pockets. On the contrary, his most startling characteristic is that he is always intensely busy......**Idleness, like kisses, to be sweet must be stolen.** [Haha : )]
- Love is like the measles; we all have to go through it.
- No, we never sicken with love twice. Cupid spends no second arrow on the same heart. 

## Essay 送你一颗子弹（刘瑜）
- 检验友谊的唯一标准就是两个人能否凑在一起说别人坏话
- 被梦想俘虏的人就是在追逐他的厄运。
- 人的每一种身份都是一种自我绑架，唯有失去是通向自由之路。
- 梦想多么妖治，多么锋利，人们在惊慌中四处逃窜，逃向功名或者利禄，或追求功名利禄而不得的怨恨。
- 好吧，疯子并不是一个政治正确的词汇，政治正确的说法应该是：那些在另一个层次实现均衡的人。均衡，我喜欢这个词，它表明一切上升或者坠落或者旋转或者破碎都有一个优雅的优点。
- 这个定居几乎是像高速列车一样向他驶过来，要把他铲进历史的垃圾堆了。事实上他已经死了，已经在腐烂了，只是生活在以倒叙的方式回放而已。
- 孤独，微渺，疯狂，无所事事，不被需要。青春的浓雾散尽以后裸露出时间的荒原。人一辈子的奋斗，不就是为了挣脱这丧心病狂的自然？

## Essay 谢谢收看（刘瑜）

- 当然有时候我也看看新闻联播，我主要是想研究我国的“领导排坐学”，“领导表情学”，“领导视察学”等领域近年有没有实现理论上的重大突破。
- 在他们怀疑人生的时候通过什么方式来找到更倒霉的人重新树立生活信心呢

## Essay 老张，亦文和蚊来（刘瑜）

- 总而言之，老张对“老张”这个词去其糟粕，取其精华地进行了发挥，使老张这个词中的社会责任感得到了充分的演绎。“亦文”最好还是滚回琼瑶阿姨的小说里去。
- 焦虑地在“喂”，“哎”，“嗨”之间颠沛流离。
- 既可去中国城扛东西，又可在地平线上诗情画意地升起。

## Essay 我爱“饭扫光”（刘瑜）

- 每到吃饭的时间，就端着空空的饭碗，遥望祖国的方向，脑子里翻滚着水煮鱼，麻辣烫，香辣蟹，等等美丽的名词，喉咙里却不断地咽着痛苦的口水，完全可以说是饮食界的文天祥。如果说阿香婆的辣是一个大老粗站在一栋居民楼下大喊；饭扫光的辣，则是张靓颖小姐的海豚音，在往上提升的过程中还有那么一点摄人心魂的震颤。

## Essay 我爱崔健（刘瑜）
- 像我这样从小到大被迫害成三好学生的人，体内得积压多少无家可归的荷尔蒙啊。
- 某个片刻一个人被表达欲击中，那个表达欲新鲜，强烈，浓郁，像一只红光满面的苹果，非常挑逗地坐在那里，让人忍不住伸出手去。
- 每个人都变成了一个纸团，被拾起来，被展开，文字凸显出来，被一个低音给念出来。贱贱地，那些高的，矮的，胖的，瘦的，老的，少的陌生人都变的有声有色，明明什么都不是，却显得像那么回事。
- 你知道吗，美好的秘诀就是速朽。

## Essay 电器（刘瑜）
- 它知道我需要它，不能把它怎么样，所以就像个妓院偷拍似的越发摆谱。
- 我的愤慨终于上升到了一种存在主义的厌世感。
- 生活就是一个手段不断淹没目的的过程，比如说吃饭问题不断淹没精神问题。
- 男人长相的几个档次：丧权辱国，闭关自守，韬光养晦，为国争光，精忠报国。
- 他就随便那么一帅，我就随便那么一赖，然后岁月流逝，我们磨磨蹭蹭的变老。
- 如果这些女孩把她们得不到的痛苦，失去的痛苦，不得其所的痛苦，统统转化成为创造性活动中的生产力，这该是生产力多么大的解放啊。
- 如果没有感情的风云变幻，我这艘快艇得在知识的海洋里飕飕地跑地多快啊！想不牛都难。
- 有时候我真的搞不清女人是真的被上帝陷害成这样，还是在用爱情来逃避更大的责任和自由。
- 如果我们不用斤来衡量芭蕾舞，用米来描述莫扎特，又怎能用一生半生，九又三分之一生来衡量爱的质地？
- 不值得书写的人生值得度过么？
- “反熵”是热力学中的一个术语，王小波同志不止一次的提起这个词，这个词的意思简而言之就是说投入的多单是释放出来的能量少，也就是“费力不讨好”的现象在物理学中表现的一种形式。
- 亚里士多德说：“人是天生的政治动物。”
- 享乐主义得以存在是又一系列公共制度的前提的，而这些前提是政治斗争的结果。以为私人生活与政治没有关系的人忘记了私人领域从边界的界定到秩序的维护都是政治问题。
- 好像唇红齿白的笑容间一颗虫牙突兀在那里。
- 人们摒弃了门外的灿烂阳光和星巴克里的资产阶级光明，趴在匈牙利咖啡馆昏暗的灯光下如同捉虱子一样费力地辨认自己书上的文字。
- 越大的自由意味着越大的责任，因为一个自由的人注定是一个精神上的孤儿，他无依无靠，除了自己的头脑和心灵。
- 空洞洞的友谊，在里面喊一声都有回音。
- 她很健忘，尤其是对自己曾经刻骨铭心的东西——好像一个小孩吃什么东西“吃伤了”。
- Tiramisu= Pick Me Up
- 一平脸上的微笑像用杆秤称过一样得体，而如意挥手的幅度也像用尺子量过一样又分寸。就是月亮也亮得很严肃，一点柔情蜜意都没有，冷冰冰，像一枚图钉。
- 任何一种关系，就像孤独，都可以上瘾。上瘾了要戒掉就很困难，但这与你爱不爱一个人没有关系。
- 好像一个日子是另一个日子在镜子里得投影。无限的镜子，无限得投影。
- 生活的属性和死亡一样，就是寂静。
- 他的脚下是纽约，一个繁华的岛屿。这个岛屿下面是地球，一颗孤独的星球。
- 这点温情，对于相爱太少，对于分手太多。她觉得自己这些年来就卡在柔软的温情和坚硬的梦想之间，飞不起来，也掉不下去。
- 没有恐惧的爱惜，就像没有牙齿的鲨鱼一样，什么都不是。
- 我，这个历史的小数点后面遥不可及一个数而已。
- 优雅，骄傲，娇憨，贤惠，活泼......各种凶器，信手拈来，无所不用其极，但是她们找不到爱情。青春的汽笛已经拉响，手上的另一张车票还是无人认领。
- 你们在一起，像头驴子，转啊转，把时间磨成粉末，然后用粉末揉面，做包子，饺子，面条，吃下去，饱了，心满意足。
- 这历史的死胡同，一路都是被揪掉的头发，踩落的球鞋，和打掉的牙齿。
- 她的想象力很发达，很像是高速公路，密密麻麻，四通八达。
- 这场辩论已经变得机械，双方所有的论点都早已深情并茂地列举完毕，现在比的就是重复的此书和音量而已。
- 又一根火柴灭了，一根一根的火柴都灭了，她在这边努力地划着火柴，他那边根本没有一根蜡烛来接应。
- 她不需要安慰，安慰太重了，她现在需要一些更轻的东西。轻的像一个摇篮曲，这样她就可以静静地睡去。
- 时间走着走着就会迷路，卡在一扇旋转门里，转来转去还在原地。
- 我对你的爱情，超出了结构功能主义的解释，存在主义的解释，阶级分析的解释，唯美主义的解释。

## Essay 其它（刘瑜）
- 仿佛一个12岁的小姑娘，偷出了妈妈的化妆品，把脸蛋涂抹的惊心动魄，对着镜子里陌生的自己，却觉得异样的熟悉。
- 它更像是一个邀请你加入舞池跳舞的女郎，要体会她的激情，你必须学会跳舞。
- 也许虚无主义只是笨蛋故作聪明的姿态。
- 我很想把这些事与人分享，但我的老公，儿子及狗都还在火星赶往地球的路上。
- 过去隆重？我还觉得这个充满规则和潜规则的世界过于啰嗦了呢。
- 总觉得那些“试验性”小说写作里，作者的自我意识太强烈了，总是要丛文字里伸出一只手来，使劲摇晃着一面旗帜，上面飘扬着两个大字——“个性”，与其说我们在读一个故事，不如说在欣赏一场行为艺术。
- 他写一个人在异域文化中的脆弱感，及从异域返回本土时同样强烈的隔阂感。
- 他紧张地盯着她的脸，看它从暮色中一点一点浮现出来，仿佛在赌场里看着抛到空中的骰子一点一点落下来。
- 她要一个现成的男人，事业是现成的，心态是现成的，可以拿着行李登上甲板就起航的轮船。

##  Essay 在平淡和奢华之间摇摆（南妮）
- 我们既希望自己享乐，又希望自己深刻。
- 在这个纷扰的时代，爱像恐龙一样难以寻觅，所以有那么多人做了工作狂
- 疲劳，产生于对需要做出反应的事物做出反应，对不想做出反应的必须反应。
- 离婚成了平庸生活的润滑剂。成了麻僵婚姻的强心针。在幻想的拒绝与悲壮里，想来一点电影女主角般的皇后况味，再来一点爱情回光返照的挣扎。
- 对于女人来说，爱情的唯美性应该是内涵与形式的高度统一。
- 上海，1000多万常住人口，几百万流动人口的远东不夜城，突然在它著名的拥挤与喧嚣中出现一个休止节拍。
- 是的是的，生前再辉煌再有名再成功再多金，死了也终于不如你乐——你至少活着，吃得动甜甜咸咸，将八卦小报看得津津有味，即使牢骚满腹，也是瓜拉松脆。因为日常生活的平静寡淡，疾病与死亡成为异常而令人注目的话题。一个人得了恶疾，在他亲戚朋友熟人同事间传播的速度之快会超出你的想象。在已经被显示出异常的人面前，自己的正常便变得格外宝贵。咀嚼这种正常带来的幸福，又更加恐惧对于不正常的恐惧。我们在面对别人的不幸时多少感到乐自己的庆幸。庆幸终究是狭隘自私浅俗市井。他们淡定空漠沉稳内倾，沉默而坚实地从事自己的工作，关注这个世界却并不轻易发表言论。**因为得懂所以慈悲。**
- 你真弄不懂骄傲与自卑是如何地铸造出了一个人的磊落风格。
- 一切先锋的实验与探讨都终有滞涩与停止吧。这是人类的可悲。令人眼花缭乱的生活观念归结起来也不过就是：结婚或者不结，生子或者不生，同居或者不同，跟旧情人恢复关系或者不恢复，玩性爱游戏或者不玩，谈爱或不谈，等等。
- 我喜欢岛。岛，三面或四面是海，明媚，清新，飘逸，空洞......对外似连非连，张力奇大；内部，却是安稳的，静谧的，悠闲的，自由规律的。
- 这个时代人们的焦灼多半是因为攀比。
- 就像有些人结婚的对象并不是他最中意的那个人，和他结婚的那个人也许是他情侣中最差劲的，他和她结婚，只是因为眼下他想结婚。他乏了，累了，玩不动了。

# Statistics                

# Self-development 

## Getting More [谈判，Stuart Diamond]
### Preface
1. 本书独特之处
      - 目标至上
      - 情感投资
      - 谈判形势判断
      - 循序渐进
      - 交换评价不同的东西：对方在意什么？
      - 对方谈判准则
      - 积极，诚心，避免操纵谈判
      - 找出问题的结症并将其转化成机会
      - 接受双方差异
      - 准备清单
1. 无形的谈判技巧
     - 同仇敌忾可以顺利建立人际关系（找到共同点：都喜欢夏天，喜欢看书等等）
     - 关注他人的想法，需求
1. 本书反对使用的技巧：赤裸裸应用权力
1. 谈判新定义
     - 迫使对方按照你的意愿行事
     - 让对方按照你的思路思考
     - 让对方理解你想让他们理解的挂念
     - 让对方感受到你想让他们感受的：出现压力风险时，人容易感情用事。当对方意识到你在意他们感受时，他们会更愿意倾听，更容易被说服。
1. 谈判目标：确定自己的谈判目标时什么，在谈判一开始就要对此做到心中有数，而且还要在谈判过程中不断提醒自己：“什么是我想在这次会议结束时想要得到而现在尚未得到的东西？”
      - 谈判目标越具体越好
      - 帮助所有相关的人实现他们的目标
      - 目标写下来随时查看
1. 步子迈小些：贪婪会让对方厌恶你，不信任你，从而使你得到的更少。本书的主题是强调“争取更多”不是“获得一切”。
1. 一切谈判与情境密切相关
      - 我的谈判目标是什么？
      - 他们是谁？
      - 要想说服他们，需要采用哪些策略和技巧？
1. 你的态度，可信度和透明度
      - 做真实的自己
## Professionalism [专业主义]
### What is professionalism? 什么是专业主义
- The Oath of Hippocrates
1. 允许我行医,我要终生奉行人道主义。 
1. 向恩师表达尊敬与感谢之意。 
1. 在行医过程中严守良心与尊严。 
1. 以患者的健康与生命为第一位。  
1. 严格为患者保守秘密。
1. 保持医学界的名誉与宝贵的传统。
1. 把同事视为兄弟;不因患者的人种、宗教、国籍和社会地位的不同而区别对待。
1. 从受孕之始,即把人的生命作为至高无上之物来尊重。
1. 无论承受怎样的压力,在运用自己的知识时也不会违背人道主义。   
专家的词源本是“profess”,意思是“向上帝发誓,以此为职业”。

- 作者列举了诸如律师、医生、教授和会计这些普遍被认为是专家的职业。对于法律这门职业作者提到：“从某种意义而言,法律是一个非常可怕的领域,它有可能仅仅依靠不同的解释而改变我们的人生。”对于会计（安然事件），医生（等候三个小时,看三分钟病），作者最后指出，单是国家认定的一张资格证并不能定义专家，“资格只不过是一张纸片而已,如果不成为 真正的专家,便如“脚底的米粒”,捡起来也不能吃。”。那么什么是专家呢？

## Love cultivation [好好修养爱，素黑]

- 先懂得为自己寻找一条路，安放好自己，追求在恋爱以外其它有意义的事情，你的心才能强壮起来，才能处理万变，才有条件和本钱去恋爱。分散恋爱的精力，才能看穿自己和爱人之间的问题。
- 谨记别强求，两个人的离合有太多无法解释或被清楚理解的原因，有种智慧需要学习，就是随缘也是爱的方式。
- 自爱应该是无条件的，正如父母应该无条件的爱孩子一样，这是天职。爱自己的人面上散发的光芒是骗不了别人的，你会活在平静，淡定，喜悦种，绝少埋怨，鲜有不满，没有太多话需要澄清，内心是一片宁静而有力量的海。
- 自爱的人不乞求被爱，反而会乐于把自己丰富的爱向别人分享，因此，自爱的人会平易近人，让人喜欢亲近，因为你的爱带着很强的感染力，等待被爱的人是焦虑的，自爱爱人的人是平和的。能爱便能被爱。  
爱是自然的发生，强求不来。
- 想获得爱情，感受活在安全感里，必须先热爱生命，这是每一个人一生必须学习和经历的成长过程。学习承受得失成败，才能变得成熟，懂得自处，然后懂得和别人相处，孕育爱。  
最好的伴侣不是别人，而是自己的内心。不能享受孤独便不能接受生命，无法好好爱自己。  
别人不好过绝对不会让你更好过。成熟的爱是在稳定的情绪，良好的身体和理性的状况下，先了解怎样爱自己，才能从容地相处，知道要和什么样的人在一起。人，从来都是孤独面对自己。未曾孤独过，捱不过孤独的人，永远不知爱的滋味，有的只是依赖的味道，跟香水差不多。涂上去的东西，都不能长久。
- 感到优越是可耻的，在这个疯狂到不可理喻的世界，麻木到只剩下互相消费的贪欲爱恨，我只感到比海更深的无助。
- 最大的幸福是活得自在、自由和喜乐，心安理得，不否定关系，也不泥守关系。当你能无须害怕或隐瞒什么，保持清醒和觉知，接受命运发生在你身上的一切，你便自由了。

## Others

- 最好学会的东西：
      1. 善待批评
      1. 基本汽车保养：引擎盖下有什么？如何换轮胎和助推启动汽车？有备用轮胎，不要让汽油少于1/4
      1. 善于回应恭维
      1. 紧跟时事
      1. 杜绝闲话
      1. 丰富阅历
      1. 习惯模棱两可
      1. 躬自厚而薄责于人
      1. 灵活应变
      1. 创造被动收入：版税，租金，专利等
      1. 有爱的能力：照顾自己照顾别人
      1. 定义好事物的界限
      1. 学习网络
      1. 确立自己的日程而不是被推到别人的日程里
      1. 创造性思考，打破常规
      1. 诚实可信

# Biography    
# Beauty&Health             
# Gender                    
# IT                        
# Law    

# Biology      
## The Selfish Gene
## Sperm Wars
## What is life [生命是什么]
### Ch1: 经典物理学家走进这个主题

- 如果给一杯水中的所有分子都做上记号，再把这杯水倒进海洋，经过彻底搅拌后使得这杯水均匀地分布在世界七大洋中；如果你从海洋中的随意一处舀出一杯水来，将会发现这杯水中大约有100个有记号的分子。  
原子用“埃”度量，1米的百亿分之一，$10^{-10}$

- 有机体的活动需要精确的物理学定义

# Data Science

##Big Data (大数据的冲击)

### What is big data

- Trend: Analyzing non-structured data

- Genernalized definition: 
    1. structured data
    2. non-structured data(text,voice,vedio,GPS,sensor)
    3. Data storage/processing/analyzing techniques: Hadoop, NoSQL, machine learning/satatistics
    4. Data Scientist/Data oriented organization

- Decide.com/FlightCaster

- Bottle neck of machine learning: store and process big data (doubt it)

* From point information to thread information 
     + Point information: purchase a product, received a service......
     + We need thread information to answer WHY!
     + Thread information: customer interaction data (non-structured or historical behavior)

     
### Walk Between Privacy and Innovation

- Collaborative Filtering (Amazon): method of making automative predictions about the interests of a user by collecting preferences or taste information from many users (collaborating). The **underline assumption** of the collaborative filtering approach is that if a person **A** has the same opinion as a person **B** on an issue, **A** is more likely to have **B**'s opinion on a different issue **X** than to have the opinion on **X** of **a person chosen randomly**.

- Rapleaf: using email address/name to get personal profile (linked to information on Facebook)

### Data Aggregator

- Pay as You Drive: car insurance (provide discount according to the driving habit)
- For company with internal technique skill: collection, cleaning, analyzing, result delivery, implementation
- Data Aggregator: provide some hard to collect off-line data (what are those?)
- Who will be data aggregator: those who develop devices for data entry and collection
- More personal, more useful, harder to get
- Payment service companies (VISA, American Express etc.): on the road to data aggregator [VISA collabrate with GAP]
- Aggregate data
     + Internal Data + External Data-->Premiun Data (multiplication effect)
     + Example: Catalina Marketing and Nilson evaluate the TV ad by studying the association between audience rating and actual purchse
     + What data to get? 
     + Example: iphone App: Nike+GPS, get running route (anonymous) and use the information to get insight for store location

### Data Scientist

- Sexy
- Characters:
     + Communication skill
     + Entrepreneuership: explore how to make data useful, lead to new data based services
     + Curiosity: not limited in art, techniques, medicine, natural science......but keenly curious about different areas. By analyzing data from differnt fields, data scientist with curiosity will find bonanza 
     
# Politics 
## Democracy in America [Tocqueville]

这本书的作者是托克维尔（1805-1859），经历过法兰西第一帝国、波旁复辟王朝、七月王朝、法兰西第二共和国、法兰西第二帝国五个“朝代”。法国著名的历史学家、社会学家、政治家。《论美国的民主》是他在35岁时写的， 之后在41岁时还写了一本经典著作《旧制度与大革命》。托克维尔是法国贵族出身的，受过很好的教育， 但是他思想倾向却是自由主义的。时至今日，没有哪个国家会承认自己是不民主的，甚至朝鲜、缅甸这样的国家也都宣称自己是民主政体。金正恩全票当选，不是还沾了个“选”字么？为什么呢？ 因为今天民主似乎成为了一种普世价值，没有人敢公然去否定民主。问题是你走的是哪种民主政治？ 如果我们不接受民主普选，那否定的理由又是什么呢？从历史上看，并不是人们不知道民主有坏处， 但关键在于这些坏处是否能够掩盖民主的价值？抑或对民主的弊端，我们应该要更多的民主还是限制民主？ 要对民主这个话题深入的理解，托克维尔的《论美国的民主》不得不读。这本书是托克维尔在美国周游一圈回到法国写的， 其中讨论了民主这种政治体制在美国实行的状况如何。书中给出的答案是，要解决民主带来的问题，我们需要更多的民主。 当时欧洲有很多保守主义者反对民主，法国大革命的血腥招致各种批评，在此情况下，这可以说是一本为民主辩护的书。

# Other 
## [Nov2015]不畏将来不念过去

- 若想改变,就从丢弃旧物开始 你留存的记忆越多,就意味着未来可以伤你的越多。你留存的记忆越细致,越是容易铸造出一个思维的牢笼,困于其中 ,越陷越深。 

> Hui: 收藏旧物无关对错，是一种生活方式。我喜欢保留旧物，人是由记忆浇灌的，为什么记忆一定是伤人的？你会被记忆所伤，说明心灵还不够强大，还没有释怀，人生就是一场修行，路漫漫其修远兮。人生从来就不完美，回避隐藏并不能让你强大，面对真相、释怀才是最终的救赎，而后自道天凉好个秋。回避是因为在乎，刻意回避反而加深了刻痕，离释怀越远。

- 到了最后,就在那个愿意放下偏见和骄傲的时候,遇见一个同样愿意的人,在一段靠谱的感情中,走向一段靠谱的婚姻
。然后,所有的剧情都落幕了,剩下的事,该来到的都来到了。不是因为你更爱谁,就可以不用面对那些鸡毛蒜皮,只
是愿意和不愿意而已。
- 欲望和天真绝无法做伴。
- 有勇气在世俗与爱情中找到平衡的人,才能相信他可以将爱情进行到底。这是我们这个时代的爱情。
- 艳遇其实就是在不提前设想、不设防的情况下发生的美丽意外,是都市人久久不敢随心而动之后,对自己内心直觉灵感的一种释放。
- 预言的自我实现:以没有确凿证据的预言为契机,唤起一种新的行动,这种行动最终使 起初的预言变为现实
- 真正的专家首先要理解专家的基本条件,然后再去思考如何成为专家。
- 我再提出一个预言——“任何人都能够成为专家”。

## Living History Farms
**Foodways**: The Ioway made use of Iowa’s prairies, rivers and wooded valleys to find food. They hunted and fished for meat. They gathered wild plants. The Ioway farmed along the rivers. Many foods were eaten fresh, while others were dried and stored for the rest of the year. The Ioway ate fresh food in season. They ate some foods raw, but also cooked many foods at ta fire pit. Each family prepared their own daily meals. Iowa women preserved food by drying it. They cut fresh meat into thin slices and hung it to dry in the sun. Ears of corn were hung from poles or speed on platforms to dry on the vine and then shell them. Squash were sliced into thin rings and hung on frames to dry. The Ioway used dried foods to make stews, the main dish in their diet. Dried meat was also pulverized and mixed with berries and animal fat to make pemmican. Dried corn could be ground into flour for breads and thickeners.

**Storing Food**: The Ioway stored dried foods in cache pits, bell-shaped holes dug into the ground. The cache pit could be up to five feet deep. Women first lined the pit with bark or grass to keep put moisture and pests. The Ioway then added ears of corn along the outside, filling the center with ben and then squash. The opening was covered by layers of animal hide, grass, planks and ashes.

## Other Notes

- After all, the wool still comes from the sheep’s back-----in the long run, whatever you’re given you pay for.
- In the end, it’s not the years in your life that count. It’s the life in your years.
- 强关系有效是因为帮助你的意愿更强；弱关系有效，是因为帮助你的能力更强。为啥？因为弱关系更可能跨界，所以求助能力的理想状态是——在不同跨界领域建立多个“强关系”。
- 什么是淫秽？Stuart法官回答：看下才知道。很多概念，在大而化之的时候都可以存在，但一追究细节，立即土崩瓦解。
- 对他人要公平，否则会触怒他人与生俱来的本能。对自己千万要记住没有什么公平。长相，身高，家世，运气，从不公平。动辄要求公平，是失败者的标配。每要一次公平就意味着你对这个世界已无计可施。
- 人类文明至今只有2个大的类型：1） 农耕文明（agriculture civilization）：土地资源决定 社会结构和权力归属；2)工商业文明（industry and business civilization）：人们摆脱了土地资源的限制，可以跨区域（cross-region）获取生存资料（living resources）。在这种文明中，金钱的力量成为决定性因素（determining factor），而权力则处于高度不稳定 。坏处是竞争太激烈。好处是精英永远有机会。
- 思想录（Pensees）——17世纪哲学家、数学家 Pascal为基督教辩护的一本书——选自其中的一句话“人类不快乐的唯一原因是不知道如何安静的呆在房间里。(The sole cause of men’s unhappiness is that he does not know how to stay quietly in his room.)”
-  生活里有我们不喜欢的人，但没有比我们身份低配不上我们的人。愿意善待眼前这个世界的人也一定会被这个世界温柔相待。
- 花太多时间去思考只有时间才能证明的威胁和承诺是一种危险的游戏。
- 一个嫉妒你的朋友比一个公然的敌人更可怕。
- 人类善于撒谎，尤其是自我欺骗。
- 没人拥有一切，珍惜并充分利用自己已经拥有的东西。
- 独处慎思，群处慎言。（Govern your thoughts when alone, and your tongue when in company.）
- 长久不快乐，人的“快乐基因”会逐渐消失，不自觉嘴角下垂眉间纹加深，这副面孔又会吓退很多原本能带给我们愉悦的人。不要成为生活中那个难以取悦的人。不快乐的原因有：1)快乐门槛高2)快乐外因多。源自于内心的喜悦简单、稳定、强大。
- 恋人常有张居安思危的脸，为小事惴惴不安。
- 内心强大的10个特质：1)being firm in your belief yet be flexible enough to change when proven wrong ; 2) being aware and cautious yet not giving a damn to everything cross my life; 3) being calm in calamity and a cracker in celebration; 4) being experienced like your grandfather yet energetic like a child; 5) being well read though knowing you still know nothing; 6)being intelligent with a strong memory yet deleting all the trash and negativity; 7) being able to observe and learn from others’ mistakes yet not fearing to make my own; 8) being the one that all look up yet not looking down upon them; 9) being able to help others yet making provisions for your own self; 10)being able to accept defeat with grace yet not resting a moment to achieve success once again
- 从狭小 的世界到广大的世界去的路上是有风浪的。——《家庭与世界》泰戈尔
- 遇到困难是生活的一部分，和困难相伴是人生的常态。生活有时就像 一张铁砂纸，由无数细小，坚韧的铁粒构成，即可磨损你的意志，也可磨亮你的人生。
- 一个女人的学识、思想、性格、格局会使你天然散发一种气味。你自身多好，价值多高，层次多大程度达到他的期望值决定了男人对你的付出和感情浓度。
- 看尽别人的故事，你一直努力做个例外，然后发现逃不出相同的结局。
- 人总怕被拒绝，但怕是无法避免的，上帝赋予你恐惧的技能。
- 对理解不了的局面退回到道德判断。
- 热情：总想和别人融为一体得到认可和安全感的情绪。
- 不是价值观，共同体这样可以说清道明的东西把人连在一起，而是无法表的的共同体验。
- 就像我们看到所有的东西一样，我们希望“看到”自己也是真实存在在这个世界上的。Nathaniel Branden (1930-2014, Canadian-American psychotherapist and writer known for his work in the psychology of self-esteem)
- Tell me who you love and I will tell you who you are.
- A wise man thinks all that he says, a fool says all that he thinks.
- 《有限与无限的游戏》把这个世界上的游戏类型分成两类：  
1.有限游戏——所有当事人同意结束，就结束了。这种游戏从属于人。小到围棋，大到战争，都是如此。  
2.无限游戏——人的存在只是为了维持游戏本身的延续。比如经济系统、人生荣耀。想伟大，就要把所有的有限游戏变成无限游戏。想快乐，就要把所有的无限游戏变成有限游戏。伟大且快乐者，在这二者之间来去自由。
- 人生来自由，却无往不在这场以有涯随无涯的博弈(all pay auction) 当中。出路有四：  
第一，不参加。  
第二，如果你一定要下注，就在目标价值以下随机下注，一次性下注，不追加下注。  
第三，如果你一定要参加多轮的全付费游戏，就得从主观上调整这个游戏对你的payoff，毕竟效用因人而异。  
第四，在不能赢的大游戏中刻画出有可能赢的小游戏。不必成为芭蕾舞明星，练练芭蕾舞，只为怡情行不行？  
一个建议对所有人都有用：不要以人生为赌注，不要把回报寄托在将来成为赢家；要让人生本身就是回报，当下就是回报，最好每一刻都是回报。当下就要快乐，最好始终都快乐。
- Uncertainty arises because of limitations in our ability to observe the world, limitations in our ability to model it, and possibly even because of innate nondeterminism.
- 一句很动人的情话：“迟早会有人举着戒指对你笑，说着余生请你多指教。”
- 如果私人领域一直无法理直气壮地言明权利边界，那么公共空间自然更加无处构建。所以，我们一直有意无意地被置于一种混沌之中。在这样的渊源之下，我们单独去强调私德、公德、教养和素质都是无效的。定义人和人之间的界限是尊重的基本条件。清楚的意识到我要的并非是你要的，己所不欲勿施于人，己所欲也并非能够随意强加于人。只有定义了边界，才能将他人作为一个独立的个体来尊重而不只是自我的延伸。
- 爱自己不是自私自利不懂宽容改变，会爱自己是指你可以完全按照自己的意愿生活，并且还能拥有别人的爱与呵护，不论单身还是已婚，这种女人的气场里总是带着温暖与惬意，更多的时候这也是一直自律和心境的比拼，赢得自己才能赢得人生。会爱自己的女人无论嫁给谁都会幸福，即便你谁也不嫁那幸福的姿态和模样也依旧会光芒万丈，你对爱自己这件事念念不忘，那么绽放和飘零就都是美。“慎独”二字也适用于对生活和情感有较高追求的女人，在没有旁人的时候也凭借高度的自觉，坚持做那个最美好也最精致的自己。不允许自己懒惰邋遢，不允许自己脆弱逃避，不允许自己没有期限的痛苦彷徨，住整洁的屋，睡温馨的床，穿干净的衣，读温暖的书，交有益的友，爱值得的人。就算这些你也需要时间努力拥有，那我也希望你的这个夜晚，会因为这些文字而展露出你最美丽的笑颜，从明天起定个短期计划先去做，能做多少做多少，唯独不要怨天尤人和自暴自弃。天生丽质的女子凤毛麟角，绝大多数的美人儿都是后天养出来的。终究不是岁月败美人，而是美人惊艳了时光。
- 在多少岁恋爱结婚不重要，重要的事和你共度余生的那个人是不是最正确的人，是值得你去珍惜并且相处起来很舒服的那个人，是你可以做真实的自己和最好的自己。好的爱情可以让人变得更好、共同成长，爱本就是两个人相互磨合的过程，如果不适合相处起来会很困难。遇不到那个人可以慢慢等，去提升自己，努力变得更优秀。要么不爱要么深爱，对自己的幸福负责，不随便牵手，不轻易承诺。遇不到真爱，是因为你活得还不够漂亮，出色的颜值包括外在的精致和内在的才华，只有当你的脸能够闪烁出迷人的气场，你心灵的丰盈才能让身边的人感受到力量，缺哪一样你都算不上活得漂亮。不要以为你变得冷漠就是你的成长，成熟的你应该变得温柔，对全世界都温柔。
- 已经失去的东西就不必再停留，成长就是一段又一段锥心的痛，不计后果的那一段叫青春，从此以后我们必须独自长大并且担负责任。过得好当下的人，是不需要忧虑未来的，当温柔已经成为了一种处事的能力，女人的才华才能尽显华彩。
- 丈夫到底是个什么东西？放在那里不打理就长荒草，天天擦一遍他又会跑，一进家就打蔫出了门来精神，在你面前浪漫风情全不懂，在别人眼里却是情圣一大个。其实没什么好不懂的，丈夫，一丈之内是你夫，一丈之外是个男人，还担当着很多的社会角色，他们需要有更广阔的天地驰骋，以便更有能力来善待家人。这个社会有钱不是万能的，没钱也是万万不能的，“能力”这个词也已不能简单的用一声“我爱你”来诠释了，成为了丈夫后,他们还需要有让妻子和孩子享受基本幸福的本领，有时候丈夫们也没什么错。如果连这一点担当与责任心都没有的话，是不配升级做丈夫的。丈夫这东西，其实就是愿意为你一个人守候的那个男人，初衷都是好的，你要相信这一点，过程都是不容易的，你要理解这一点。
- 一半算是自嘲，一半算是抖落一下世俗生活的尘土——做雅痞这件事儿，其实的确还是挺辛苦的。
- 话糙理不糙，人生如妓，努力达到角色与体验的高度统一，才是正道。
- 不要评价一个人的出身，因为这无法改变；**不要评价一个人的遭遇，因为你不知道他的故事**。**不要评价一个人的感情，除非你参与了他的人生**。与其关注一个人的未来，不如是踏踏实实做好自己。
- 《西西里的美丽传说》里，莫妮卡·贝鲁奇的丈夫死在了战场，而她作为一个美艳的寡妇，失去了男人的保护，也没有任何经济来源，她于是只有通过出卖身体换面包吃。在那个战争年代，人都是很矛盾的——男人都想得到她，却纷纷假装厌弃她；女人都想成为她，却都想扑上去摧毁她，在背后毁灭她。其实她没有什么过错，她最大的过错就是生的太过美丽。
- “大家一定要小心那些有六块腹肌的男人和永远保持好身材的女人，这些人拥有你所想不到的决心和意志力。想一想大白天里，他们能“唰”的一下从床上爬起来，到外面跑上几圈。多可怕啊！他们什么事都能干得出来。这绝对不是一个笑话，但凡是有一副好身材的人，活得都不会太差。”
- 变态的工作关系也是应该避免的，你们要特别避免在你们不崇敬或者不想像他一样的人手下干活，那是很危险的。所有人在某种程度上都受到权威人物的控制，尤其是那些为我们提供回报的权威人物。在我年轻的时候，我的办法是找出我尊敬的人，然后想办法调到他手下去。在你们正确地仰慕的人手下工作，在生活中取得的成就将会更加令人满意。
- 在遭遇一件令你难以接受的悲剧时，你永远也不能因为摆脱不掉它的困扰、在生活中再屡遭失败而让这一件悲剧变成两件、三件。
- 复杂的官僚程序不是文明社会的最好制度。更好的制度是一张无缝的、非官僚的信任之网。
- 如果你的思维完全依赖于他人，只要一超出你的领域，就求助专家建议，那么你将遭受很多灾难。
- 技术从来不是人性的反面。  
技术只是人类机体的延伸。  
技术是人性最充分的显现。  
技术如果出问题，是人性本身出问题。
- 《死时谁为你哭泣》的作者罗宾·夏玛说：“不是因为某件事很难，你才不想做，而是因为你不想做，让这件事变得很难。”
- 有民主就不会有财富上的平均分配，平均按需分配是社会主义国家假想的现象。民主意味着一种精神上的平等，决定权上的平等，但在此基础上，人便会自动在财富的分配上区别开来，除非认为强制分配，否则无法平均，因为人的能力，品格和运气各不相同。
- 找到适合自己的工作与生活的平衡方式。人要取得平衡，不在于每天花多长时间工作、又能余下多长时间过自己的生活，而是在于你的选择：在于选择要什么、选择做什么、选择如何有质量的去做到，也在于你是否能寻求到内心的那份安宁与坦然。
- 培养并尊重内心的直觉。是的，在战术层面上，数据非常有用，但是，在战略层面，一个卓越的市场人的直觉同样可贵。因为他们的直觉能让公司看到数据看不到的东西——那些深藏在消费者心里的东西。例如：品牌的定位（是应该聚焦在一个诉求还是更多），品牌/产品的命名，一个品类到底需要多少个品牌才能获取最大市场份额等等。
- 爱情就是两个人一起犯贱，突然一个人不犯了，另一个就SB了。
- 说走就走是人生最华美的奢侈，也是最灿烂的自由。
- If you don't understand my silence, you will never understand my words.
- 人生自古谁无死，贱人先死我后死。
- 幸福如人饮水，冷暖自知。你不是别人，怎知那人走过的路，心中的乐与苦。
- 时间不知不觉，我们后知后觉。
- 认知没有什么终极正确，只有逐步升级。认知的升级，本质上来源于认知尺度的扩展。
      1.时间尺度——多读历史。
      2.空间尺度——多观世界。
      3.观念尺度——聆听高人。
认知没有正误之别。但确实有高下之分。因为所在尺度层次有异。
- **[机会成本]** 我做的事情价值多少，是由我放弃的事情反映出来的，而我放弃的事情，也是由我做的事情的价值反映的。同样的资源你怎么分，同样的抉择你怎么选，将一个人的层次或者说特质表露无疑。在你实际行动的诠释下，一切的言语都是很苍白无力的： _你做了什么，你就是什么，值什么_。
- 我与巴菲特工作这么多年，他这个人的优点之一是他总是自觉地从决策树的角度思考问题，并从数学的排列与组合的角度思考问题。
- 阅读本身并不是力量的来源，因为阅读所触发的思考和情绪才是。阅读一篇文章，触动一种情绪，持久保留下的是这种被触动的情绪而不是文章本身。一门学问最终要被转化成见识和技能保留下来。系统知识更多是在代与代的传递时才更加重要。
- 怎样拥有一学就是十几个小时的精力？
      - **增加精力储量:** 健康饮食，适度锻炼，充足睡眠。主动、适时地在疲劳之前及时地休息，调整好状态之后再开始学习和工作而不是强制自己学习，可以有效地延长我们的工作时间。
      - **减少精力的消耗:** 困难的、陌生的、缺乏主观意愿、反馈周期时间长、没有正反馈的事情消耗人的精力就比较严重。防止出现严重的自责情绪。越熟悉，消耗的精力会越少。尽量在熟悉的环境，把生活琐事都变成习惯和规律，尽量减少杂乱事务对自己精力的消耗，把自己旺盛的高质量的精力都投注到学习和工作上。

